### 2015-11-14 docs/tm-abstract.tex
added abstract paper and tex file

\documentclass[a4paper]{article}
\usepackage[usenames]{color} %used for font color
\usepackage{hyperref}
\title{Location Extraction based on Tweets, without an external datasource}
\author{Erdi \c{C}all{\i}\\s4600673}
\date{27 September 2015}

\begin{document}

\maketitle
\section*{Research Question}
Is it possible to extract location from Tweets without using an external data source?
\section*{Description}
In this study I want to try to classify twitter users with locations, only using the data provided by twitter. I don't think I can create a very high precision algorithm in the context of this research, but I want to show that, using this method, we can get to a precision and I want to discuss how it can be improved or why it did not work. I'm not planning on using any external data source (e.g. Foursquare) to tag user locations, as some of the other studies\footnote{http://www3.ntu.edu.sg/home/axsun/paper/Sigir14Petar\_CR.pdf} do. 
\section*{Data}
Twitter users can select to share their location and Twitter provides geo-location data for those tweets.
\section*{Method}
I'm planning on applying the $LDA$ algorithm on geo-tagged tweets with a hope to find an underlying topic model for different locations. I'm also planning on trying a \href{https://github.com/kzhai/InfVocLDA}{\underline{Streaming LDA implementation}}. Which would serve the purpose of updating location topic model and possibly user locations over time.
\end{document}

### 2015-11-15 reader.py
added settings.py and read twitter configurations Added python-twitter to requirements implemented reader.py to read stream samples with geo location implemented a simple runner script

@@ -1,0 +1,19 @@
+import twitter
+
+from settings import config
+
+
+class TweetReader:
+    def __init__(self):
+        self.api = twitter.Api(consumer_key=config['consumer_key'],
+                               consumer_secret=config['consumer_secret'],
+                               access_token_key=config['access_token'],
+                               access_token_secret=config['access_token_secret'])
+
+    def get_tweet_samples_with_location(self):
+        samples = self.api.GetStreamSample()
+
+        for sample in samples:
+            if 'contributors' in sample:  # this is a tweet
+                if sample['geo'] is not None and sample['geo']['type'] == u"Point":
+                    yield sample

### 2015-11-15 run.py

@@ -1,0 +1,5 @@
+from reader import TweetReader
+
+reader = TweetReader()
+for sample in reader.get_tweet_samples_with_location():
+    print sample

### 2015-11-15 settings.py

@@ -1,0 +1,10 @@
+import ConfigParser
+
+configParser = ConfigParser.RawConfigParser()
+configParser.read('config')
+
+config = dict()
+config['consumer_key'] = configParser.get('twitter', 'consumer_key')
+config['consumer_secret'] = configParser.get('twitter', 'consumer_secret')
+config['access_token'] = configParser.get('twitter', 'access_token')
+config['access_token_secret'] = configParser.get('twitter', 'access_token_secret')

### 2015-11-15 reader.py
defined twitter specific config file in settings.

@@ -1,14 +1,12 @@
 import twitter
 
-from settings import config
-
 
 class TweetReader:
-    def __init__(self):
-        self.api = twitter.Api(consumer_key=config['consumer_key'],
-                               consumer_secret=config['consumer_secret'],
-                               access_token_key=config['access_token'],
-                               access_token_secret=config['access_token_secret'])
+    def __init__(self, twitter_config):
+        self.api = twitter.Api(consumer_key=twitter_config['consumer_key'],
+                               consumer_secret=twitter_config['consumer_secret'],
+                               access_token_key=twitter_config['access_token'],
+                               access_token_secret=twitter_config['access_token_secret'])
 
     def get_tweet_samples_with_location(self):
         samples = self.api.GetStreamSample()

### 2015-11-15 run.py

@@ -1,5 +1,7 @@
 from reader import TweetReader
+from settings import twitter_config
 
-reader = TweetReader()
+reader = TweetReader(twitter_config)
+
 for sample in reader.get_tweet_samples_with_location():
     print sample

### 2015-11-15 settings.py

@@ -3,8 +3,8 @@ import ConfigParser
 configParser = ConfigParser.RawConfigParser()
 configParser.read('config')
 
-config = dict()
-config['consumer_key'] = configParser.get('twitter', 'consumer_key')
-config['consumer_secret'] = configParser.get('twitter', 'consumer_secret')
-config['access_token'] = configParser.get('twitter', 'access_token')
-config['access_token_secret'] = configParser.get('twitter', 'access_token_secret')
+twitter_config = dict()
+twitter_config['consumer_key'] = configParser.get('twitter', 'consumer_key')
+twitter_config['consumer_secret'] = configParser.get('twitter', 'consumer_secret')
+twitter_config['access_token'] = configParser.get('twitter', 'access_token')
+twitter_config['access_token_secret'] = configParser.get('twitter', 'access_token_secret')

### 2015-11-15 settings.py
added mongo configuration

@@ -8,3 +8,7 @@ twitter_config['consumer_key'] = configParser.get('twitter', 'consumer_key')
 twitter_config['consumer_secret'] = configParser.get('twitter', 'consumer_secret')
 twitter_config['access_token'] = configParser.get('twitter', 'access_token')
 twitter_config['access_token_secret'] = configParser.get('twitter', 'access_token_secret')
+
+mongod_config = dict()
+mongod_config['connection_string'] = configParser.get('mongod', 'connection_string')
+mongod_config['database_name'] = configParser.get('mongod', 'database_name')

### 2015-11-15 data.py
implemented mongodb class and write_stream

@@ -1,0 +1,16 @@
+# coding=utf-8
+
+from pymongo import MongoClient
+
+
+class MongoDB:
+    tweets_collection = 'tweets'
+
+    def __init__(self, mongodb_config):
+        self.client = MongoClient(mongodb_config['connection_string'])
+        self.db = self.client[mongodb_config['database_name']]
+        self.tweets_collection = self.db[MongoDB.tweets_collection]
+
+    def write_stream(self, stream):
+        for batch in stream:
+            self.tweets_collection.insert_many(batch)

### 2015-11-15 run.py

@@ -1,7 +1,8 @@
+from data import MongoDB
 from reader import TweetReader
-from settings import twitter_config
+from settings import twitter_config, mongod_config
 
+mongodb = MongoDB(mongod_config)
 reader = TweetReader(twitter_config)
 
-for sample in reader.get_tweet_samples_with_location():
-    print sample
+mongodb.write_stream(reader.get_sample_stream_with_location())

### 2015-11-15 helpers.py
implemented chunked streams

@@ -1,0 +1,20 @@
+class ChunkedStream:
+    def __init__(self, chunk_size=10, total_chunks=10):
+        self.chunk_size = chunk_size
+        self.total_chunks = total_chunks
+        self.stream = None
+
+    def __call__(self, f):
+        def wrapped_f(*args):
+            self.stream = f(*args)
+
+            chunk_count = 0
+            current_chunk = []
+            while chunk_count < self.total_chunks:
+                current_chunk.append(self.stream.next())
+                if len(current_chunk) >= self.chunk_size:
+                    yield current_chunk
+                    current_chunk = []
+                    chunk_count += 1
+
+        return wrapped_f

### 2015-11-15 reader.py

@@ -1,4 +1,5 @@
 import twitter
+from helpers import ChunkedStream
 
 
 class TweetReader:
@@ -8,10 +9,17 @@ class TweetReader:
                                access_token_key=twitter_config['access_token'],
                                access_token_secret=twitter_config['access_token_secret'])
 
-    def get_tweet_samples_with_location(self):
-        samples = self.api.GetStreamSample()
+    def get_sample_stream(self):
+        return self.api.GetStreamSample()
 
-        for sample in samples:
+    @ChunkedStream(chunk_size=2)
+    def get_sample_stream_with_location(self):  # training data
+        stream = self.get_sample_stream()
+        for sample in stream:
             if 'contributors' in sample:  # this is a tweet
                 if sample['geo'] is not None and sample['geo']['type'] == u"Point":
+                    print("yielding")
                     yield sample
+
+
+

### 2015-11-15 data.py
formatted and added encoding to files

@@ -1,5 +1,4 @@
 # coding=utf-8
-
 from pymongo import MongoClient
 
 

### 2015-11-15 helpers.py

@@ -1,3 +1,4 @@
+# coding=utf-8
 class ChunkedStream:
     def __init__(self, chunk_size=10, total_chunks=10):
         self.chunk_size = chunk_size

### 2015-11-15 reader.py

@@ -1,4 +1,6 @@
+# coding=utf-8
 import twitter
+
 from helpers import ChunkedStream
 
 
@@ -20,6 +22,3 @@ class TweetReader:
                 if sample['geo'] is not None and sample['geo']['type'] == u"Point":
                     print("yielding")
                     yield sample
-
-
-

### 2015-11-15 run.py

@@ -1,3 +1,4 @@
+# coding=utf-8
 from data import MongoDB
 from reader import TweetReader
 from settings import twitter_config, mongod_config

### 2015-11-15 settings.py

@@ -1,3 +1,4 @@
+# coding=utf-8
 import ConfigParser
 
 configParser = ConfigParser.RawConfigParser()

### 2015-11-15 helpers.py
added chunk configuration

@@ -1,8 +1,12 @@
 # coding=utf-8
+from settings import streaming_config
+
+
 class ChunkedStream:
-    def __init__(self, chunk_size=10, total_chunks=10):
-        self.chunk_size = chunk_size
-        self.total_chunks = total_chunks
+
+    def __init__(self):
+        self.chunk_size = streaming_config["chunk_size"]
+        self.total_chunks = streaming_config["total_chunks"]
         self.stream = None
 
     def __call__(self, f):

### 2015-11-15 reader.py

@@ -14,7 +14,7 @@ class TweetReader:
     def get_sample_stream(self):
         return self.api.GetStreamSample()
 
-    @ChunkedStream(chunk_size=2)
+    @ChunkedStream()
     def get_sample_stream_with_location(self):  # training data
         stream = self.get_sample_stream()
         for sample in stream:

### 2015-11-15 settings.py

@@ -13,3 +13,7 @@ twitter_config['access_token_secret'] = configParser.get('twitter', 'access_toke
 mongod_config = dict()
 mongod_config['connection_string'] = configParser.get('mongod', 'connection_string')
 mongod_config['database_name'] = configParser.get('mongod', 'database_name')
+
+streaming_config = dict()
+streaming_config['chunk_size'] = int(configParser.get('streaming', 'chunk_size'))
+streaming_config['total_chunks'] = int(configParser.get('streaming', 'total_chunks'))

### 2015-11-15 helpers.py
added infinite chunks option with total_chunks = -1

@@ -15,7 +15,7 @@ class ChunkedStream:
 
             chunk_count = 0
             current_chunk = []
-            while chunk_count < self.total_chunks:
+            while chunk_count < self.total_chunks or self.total_chunks != -1:
                 current_chunk.append(self.stream.next())
                 if len(current_chunk) >= self.chunk_size:
                     yield current_chunk

### 2015-11-15 reader.py
meaningful comment added for training data generator

@@ -14,6 +14,7 @@ class TweetReader:
     def get_sample_stream(self):
         return self.api.GetStreamSample()
 
+    # Training Data
     @ChunkedStream()
     def get_sample_stream_with_location(self):  # training data
         stream = self.get_sample_stream()

### 2016-01-08 sklearn_comparison.py
removed unnecessary print line

@@ -199,7 +199,6 @@ def run_after_progress():
 
 
 if __name__ == "__main__":
-    print sys.argv[1]
     if len(sys.argv) > 0:
         main(sys.argv[1])
     else:

### 2016-01-08 sklearn_comparison.py
ability to run in non-gcloud instances.

@@ -156,14 +156,16 @@ classifier_names = [
 ]
 
 execution = Execution()
-instance_meta = gcloud.get_metadata()
+instance_meta = {}
 corpus = Corpus()
+
 
 def main(classifier=None):
     if classifier is None:
         for index in range(0, len(classifiers)):
             run_classifier_with_id(index)
     elif classifier == "all-gcloud":
+        super.instance_meta = gcloud.get_metadata()
         run_after_progress()
     else:
         run_classifier_with_id(int(classifier))

### 2016-01-08 sklearn_comparison.py
removed non-sparse algorithms

@@ -1,14 +1,12 @@
 import sys
 from datetime import datetime
 
-from sklearn.discriminant_analysis import LinearDiscriminantAnalysis
-from sklearn.ensemble import GradientBoostingClassifier, AdaBoostClassifier
-from sklearn.gaussian_process import GaussianProcess
+from sklearn.ensemble import AdaBoostClassifier
 from sklearn.linear_model import LogisticRegressionCV, SGDClassifier, RidgeCV, LinearRegression, LassoCV, ElasticNetCV, \
-    MultiTaskLassoCV, BayesianRidge, ARDRegression, Perceptron, PassiveAggressiveClassifier
-from sklearn.naive_bayes import GaussianNB, MultinomialNB, BernoulliNB
+    Perceptron, PassiveAggressiveClassifier
+from sklearn.naive_bayes import MultinomialNB, BernoulliNB
 from sklearn.neighbors import KNeighborsClassifier, RadiusNeighborsClassifier
-from sklearn.svm import SVC, NuSVC, LinearSVC
+from sklearn.svm import SVC, LinearSVC
 from sklearn.tree import DecisionTreeClassifier
 
 import gcloud
@@ -20,9 +18,6 @@ classifiers = [
     RidgeCV(alphas=[.1, .5, 1, 5, 10]),
     LassoCV(),
     ElasticNetCV(),
-    MultiTaskLassoCV(),
-    BayesianRidge(),
-    ARDRegression(),
     LogisticRegressionCV(),
     SGDClassifier(loss="hinge"),
     SGDClassifier(loss="log"),
@@ -36,52 +31,17 @@ classifiers = [
     Perceptron(),
     PassiveAggressiveClassifier(loss="hinge"),
     PassiveAggressiveClassifier(loss="squared_hinge"),
-    LinearDiscriminantAnalysis(),
-    LinearDiscriminantAnalysis(solver="lsqr"),
-    LinearDiscriminantAnalysis(solver="eigen"),
     SVC(kernel='poly'),
     SVC(kernel='sigmoid'),
-    SVC(kernel='precomputed'),
-    NuSVC(),
     LinearSVC(),
     KNeighborsClassifier(n_neighbors=8, weights="uniform"),
     KNeighborsClassifier(n_neighbors=8, weights="distance"),
     RadiusNeighborsClassifier(weights="uniform"),
     RadiusNeighborsClassifier(weights="distance"),
-    GaussianProcess(regr="constant", optimizer="fmin_cobyla", corr="absolute_exponential"),
[…]

### 2016-01-08 analysis/SKLearn.py
added location counts to results. calculating it everytime is not useful but it's ok

@@ -1,7 +1,7 @@
 import numpy
 from sklearn.feature_extraction.text import CountVectorizer, TfidfTransformer
 
-import settings
+from settings import locations
 from data.Data import Data
 
 
@@ -12,7 +12,12 @@ class ClassifierExecutor:
     def execute(self, training, test):
         self.classifier.fit(training['tfidfs'], training['document_labels'])
         predicted = self.classifier.predict(test['tfidfs'])
-        return numpy.mean(predicted == test['document_labels'])
+        result = {"precision": numpy.mean(predicted == test['document_labels']), "predicted": {}, "actual": {}}
+
+        for location in locations.keys():
+            result["predicted"][location] = numpy.count_nonzero(predicted == locations[location])
+            result["actual"][location] = numpy.count_nonzero(test['document_labels'] == locations[location])
+        return result
 
 
 class DataVectorizer:
@@ -35,7 +40,7 @@ class DataVectorizer:
         document_labels = []
         for doc in docs:
             full_name = doc['place']['full_name']
-            document_label_index = settings.locations[full_name]
+            document_label_index = locations[full_name]
             for tweet in doc['timeline']:
                 documents.append(tweet['text'])
                 document_labels.append(document_label_index)

### 2016-01-09 analysis/SKLearn.py
added binary classification option.

@@ -6,8 +6,9 @@ from data.Data import Data
 
 
 class ClassifierExecutor:
-    def __init__(self, classifier):
+    def __init__(self, classifier, binary_classification=False):
         self.classifier = classifier
+        self.binary_classification = binary_classification
 
     def execute(self, training, test):
         self.classifier.fit(training['tfidfs'], training['document_labels'])
@@ -21,9 +22,10 @@ class ClassifierExecutor:
 
 
 class DataVectorizer:
-    def __init__(self, ngram_range=(1, 2)):
+    def __init__(self, ngram_range=(1, 2), binary_classification=False):
         self.vectorizer = CountVectorizer(min_df=1, ngram_range=ngram_range)
         self.tfidf_transformer = TfidfTransformer()
+        self.binary_classification = binary_classification
 
     def convert(self, training_docs, test_docs):
         training_corpus = self.__create_corpus__(training_docs)
@@ -40,7 +42,12 @@ class DataVectorizer:
         document_labels = []
         for doc in docs:
             full_name = doc['place']['full_name']
-            document_label_index = locations[full_name]
+
+            if self.binary_classification:
+                document_label_index = full_name == "Manhattan, NY"
+            else:
+                document_label_index = locations[full_name]
+
             for tweet in doc['timeline']:
                 documents.append(tweet['text'])
                 document_labels.append(document_label_index)
@@ -48,14 +55,15 @@ class DataVectorizer:
 
 
 class Corpus:
-    def __init__(self):
+    def __init__(self, binary_classification=False):
         self.underlying = None
         self.initialized = False
+        self.binary_classification = binary_classification
 
     def get(self):
         if not self.initialized:
             data = Data()
-            vectorizer = DataVectorizer()
+            vectorizer = DataVectorizer(binary_classification=self.binary_classification)
             self.underlying = vectorizer.convert(data.get_training_data(), data.get_test_data())
             self.initialized = True
         return self.underlying

### 2016-01-09 sklearn_comparison.py

@@ -75,9 +75,10 @@ classifier_names = [
     'AdaBoostClassifier(n_estimators=170)',
 ]
 
+binary_classification = False
 execution = Execution()
 instance_meta = {}
-corpus = Corpus()
+corpus = Corpus(binary_classification=binary_classification)
 
 
 def main(classifier=None):
@@ -92,7 +93,7 @@ def main(classifier=None):
 
 
 def run_classifier_with_id(classifier_id):
-    executor = ClassifierExecutor(classifiers[classifier_id])
+    executor = ClassifierExecutor(classifiers[classifier_id], binary_classification=binary_classification)
     result = {"classifier": classifier_names[classifier_id], "classifier_id": classifier_id,
               "started_at": datetime.now(), "meta": instance_meta}
     execution.write_progress(result)

### 2016-01-09 analysis/SKLearn.py
normalised data by fixing the number of documents per class

@@ -36,6 +36,43 @@ class DataVectorizer:
         test_corpus['tfidfs'] = self.tfidf_transformer.transform(self.vectorizer.transform(test_corpus['documents']))
         return {"training": training_corpus, "test": test_corpus}
 
+    def normalise(self, docs):
+        normalised_docs = {"document_labels": [], "documents": []}
+        if self.binary_classification:
+            positives = sum(docs["document_labels"])
+            negatives = len(docs["document_labels"]) - positives
+            positive_count = 0
+            negative_count = 0
+            limit = positives if positives < negatives else negatives
+            count = 0
+            while positive_count < limit or negative_count < limit:
+                label = docs["document_labels"][count]
+                positive_count += label
+                negative_count += not label
+                if (label and positive_count < limit) or (not label and negative_count < limit):
+                    normalised_docs["document_labels"].append(label)
+                    normalised_docs["documents"].append(docs["documents"][count])
+                count += 1
+        else:
+            location_counts = Dictrement()
+            for label in docs["document_labels"]:
+                location_counts.increment(label)
+            limit = sys.maxint
+            for label in location_counts.underlying.keys():
+                if location_counts.get(label) < limit:
+                    limit = location_counts.get(label)
+            count = 0
+            number_of_docs = len(docs["document_labels"])
+            new_counts = Dictrement()
+            while count < number_of_docs:
+                label = docs["document_labels"][count]
+                if new_counts.get(label) < limit:
+                    normalised_docs["document_labels"].append(label)
+                    normalised_docs["documents"].append(docs["documents"][count])
+                    new_counts.increment(label)
+                count += 1
+
+        return normalised_docs
     @staticmethod
     def __create_corpus__(docs):
         documents = []

### 2016-01-09 analysis/SKLearn.py
precision_recall_fscore_support results.

@@ -1,24 +1,30 @@
 import numpy
 from sklearn.feature_extraction.text import CountVectorizer, TfidfTransformer
+from sklearn.metrics import precision_recall_fscore_support
 
-from settings import locations
 from data.Data import Data
+from helpers import Dictrement
+from settings import locations
 
 
 class ClassifierExecutor:
     def __init__(self, classifier, binary_classification=False):
         self.classifier = classifier
         self.binary_classification = binary_classification
+        if binary_classification:
+            self.labels = [0, 1]
+        else:
+            self.labels = locations.values()
 
     def execute(self, training, test):
         self.classifier.fit(training['tfidfs'], training['document_labels'])
         predicted = self.classifier.predict(test['tfidfs'])
-        result = {"precision": numpy.mean(predicted == test['document_labels']), "predicted": {}, "actual": {}}
-
-        for location in locations.keys():
-            result["predicted"][location] = numpy.count_nonzero(predicted == locations[location])
-            result["actual"][location] = numpy.count_nonzero(test['document_labels'] == locations[location])
-        return result
+        measures = precision_recall_fscore_support(predicted, test['document_labels'], labels=self.labels)
+        return {"precision": map(str, measures[0]),  # why can't you encode these floats py/mongo?
+                "recall": map(str, measures[1]),
+                "f1score": map(str, measures[2]),
+                "support": map(str, measures[3]),
+                "labels": str(self.labels)}
 
 
 class DataVectorizer:
@@ -28,9 +34,12 @@ class DataVectorizer:
         self.binary_classification = binary_classification
 
     def convert(self, training_docs, test_docs):
-        training_corpus = self.__create_corpus__(training_docs)
-        test_corpus = self.__create_corpus__(test_docs)
-
+        training_corpus = self.normalise(self.__create_corpus_from_tagged_tweets__(training_docs))
+        test_corpus = self.normalise(self.__create_corpus_from_tagged_tweets__(test_docs))
+        print sum(training_corpus["document_labels"])
+        print len(training_corpus["document_labels"])
+        print sum(test_corpus["document_labels"])
+        print len(test_corpus["document_labels"])
         training_corpus['tfidfs'] = self.tfidf_transformer.fit_transform(
                 self.vectorizer.fit_transform(training_corpus['documents']))
         test_corpus['tfidfs'] = self.tfidf_transformer.transform(self.vectorizer.transform(test_corpus['documents']))

### 2016-01-09 sklearn_comparison.py

@@ -98,12 +98,11 @@ def run_classifier_with_id(classifier_id):
               "started_at": datetime.now(), "meta": instance_meta}
     execution.write_progress(result)
     try:
-        precision = executor.execute(corpus.get_training(), corpus.get_test())
-        print "%s: %.4f" % (classifier_names[classifier_id], precision)
-        result['precision'] = precision
+        result['result'] = executor.execute(corpus.get_training(), corpus.get_test())
+        print "%s\n%s" % (classifier_names[classifier_id], str(result["result"]))
     except Exception as e:
         print "%s: %s" % (classifier_names[classifier_id], e)
-        result['exception'] = str(e)
+        result['exception'] = str(sys.exc_info())
     result['ended_at'] = datetime.now()
     result['execution_time'] = str(result['ended_at'] - result['started_at'])
     execution.write_execution_result(result)

### 2016-01-09 analysis/SKLearn.py
added option to include user history.

@@ -1,4 +1,5 @@
-import numpy
+import sys
+
 from sklearn.feature_extraction.text import CountVectorizer, TfidfTransformer
 from sklearn.metrics import precision_recall_fscore_support
 
@@ -28,14 +29,15 @@ class ClassifierExecutor:
 
 
 class DataVectorizer:
-    def __init__(self, ngram_range=(1, 2), binary_classification=False):
+    def __init__(self, ngram_range=(1, 2), binary_classification=False, include_user_history=True):
         self.vectorizer = CountVectorizer(min_df=1, ngram_range=ngram_range)
         self.tfidf_transformer = TfidfTransformer()
         self.binary_classification = binary_classification
+        self.include_user_history = include_user_history
 
     def convert(self, training_docs, test_docs):
-        training_corpus = self.normalise(self.__create_corpus_from_tagged_tweets__(training_docs))
-        test_corpus = self.normalise(self.__create_corpus_from_tagged_tweets__(test_docs))
+        training_corpus = self.normalise(self.__create_corpus__(training_docs))
+        test_corpus = self.normalise(self.__create_corpus__(test_docs))
         print sum(training_corpus["document_labels"])
         print len(training_corpus["document_labels"])
         print sum(test_corpus["document_labels"])
@@ -82,8 +84,8 @@ class DataVectorizer:
                 count += 1
 
         return normalised_docs
-    @staticmethod
-    def __create_corpus__(docs):
+
+    def __create_corpus_from_history__(self, docs):
         documents = []
         document_labels = []
         for doc in docs:
@@ -99,17 +101,38 @@ class DataVectorizer:
                 document_labels.append(document_label_index)
         return {"document_labels": document_labels, "documents": documents}
 
+    def __create_corpus_from_tweets__(self, docs):
+        documents = []
+        document_labels = []
+        for doc in docs:
+            full_name = doc['place']['full_name']
+
+            if self.binary_classification:
+                document_label_index = full_name == "Manhattan, NY"
+            else:
+                document_label_index = locations[full_name]
+
+            documents.append(doc['text'])
+            document_labels.append(document_label_index)
+        return {"document_labels": document_labels, "documents": documents}
+
+    def __create_corpus__(self, docs):
+        if self.include_user_history:
+            return self.__create_corpus_from_history__(docs)
+        else:
+            return self.__create_corpus_from_tweets__(docs)
 
 class Corpus:
-    def __init__(self, binary_classification=False):
[…]

### 2016-01-09 sklearn_comparison.py

@@ -76,9 +76,10 @@ classifier_names = [
 ]
 
 binary_classification = False
+include_user_history = False
 execution = Execution()
 instance_meta = {}
-corpus = Corpus(binary_classification=binary_classification)
+corpus = Corpus(binary_classification=binary_classification, include_user_history=include_user_history)
 
 
 def main(classifier=None):

### 2016-01-09 analysis/SKLearn.py
reformat and minor bugfix on execution script

@@ -122,6 +122,7 @@ class DataVectorizer:
         else:
             return self.__create_corpus_from_tweets__(docs)
 
+
 class Corpus:
     def __init__(self, binary_classification=False, include_user_history=True):
         self.underlying = None
@@ -132,7 +133,8 @@ class Corpus:
     def get(self):
         if not self.initialized:
             data = Data(include_user_history=self.include_user_history)
-            vectorizer = DataVectorizer(binary_classification=self.binary_classification, include_user_history=self.include_user_history)
+            vectorizer = DataVectorizer(binary_classification=self.binary_classification,
+                                        include_user_history=self.include_user_history)
             self.underlying = vectorizer.convert(data.get_training_data(), data.get_test_data())
             self.initialized = True
         return self.underlying

### 2016-01-09 sklearn_comparison.py

@@ -122,7 +122,7 @@ def run_after_progress():
 
 
 if __name__ == "__main__":
-    if len(sys.argv) > 0:
+    if len(sys.argv) > 1:
         main(sys.argv[1])
     else:
         main()

### 2016-01-10 docs/paper.tex
added "science" template

% Use only LaTeX2e, calling the article.cls class and 12-point type.

\documentclass[12pt]{article}

% Users of the {thebibliography} environment or BibTeX should use the
% scicite.sty package, downloadable from *Science* at
% www.sciencemag.org/about/authors/prep/TeX_help/ .
% This package should properly format in-text
% reference calls and reference-list numbers.

\usepackage{scicite}

% Use times if you have the font installed; otherwise, comment out the
% following line.

\usepackage{times}

% The preamble here sets up a lot of new/revised commands and
% environments.  It's annoying, but please do *not* try to strip these
% out into a separate .sty file (which could lead to the loss of some
% information when we convert the file to other formats).  Instead, keep
% them in the preamble of your main LaTeX source file.

% The following parameters seem to provide a reasonable page setup.

\topmargin 0.0cm
\oddsidemargin 0.2cm
\textwidth 16cm
\textheight 21cm
\footskip 1.0cm

%The next command sets up an environment for the abstract to your paper.

\newenvironment{sciabstract}{%
\begin{quote} \bf}
{\end{quote}}

% If your reference list includes text notes as well as references,
% include the following line; otherwise, comment it out.

\renewcommand\refname{References and Notes}

% The following lines set up an environment for the last note in the
% reference list, which commonly includes acknowledgments of funding,
% help, etc.  It's intended for users of BibTeX or the {thebibliography}
% environment.  Users who are hand-coding their references at the end
% using a list environment such as {enumerate} can simply add another
% item at the end, and it will be numbered automatically.

\newcounter{lastnote}
\newenvironment{scilastnote}{%
\setcounter{lastnote}{\value{enumiv}}%
\addtocounter{lastnote}{+1}%
\begin{list}%
{\arabic{lastnote}.}
{\setlength{\leftmargin}{.22in}}
{\setlength{\labelsep}{.5em}}}
{\end{list}}

% Include your paper's title here

\title{A simple {\it Science\/} Template}

% Place the author information here.  Please hand-code the contact
% information and notecalls; do *not* use \footnote commands.  Let the
% author contact information appear immediately below the author names
% as shown.  We would also prefer that you don't change the type-size
% settings shown here.

\author
{John Smith,$^{1\ast}$ Jane Doe,$^{1}$ Joe Scientist$^{2}$\\
\\
\normalsize{$^{1}$Department of Chemistry, University of Wherever,}\\
\normalsize{An Unknown Address, Wherever, ST 00000, USA}\\
\normalsize{$^{2}$Another Unknown Address, Palookaville, ST 99999, USA}\\
\\
\normalsize{$^\ast$To whom correspondence should be addressed; E-mail:  jsmith@wherever.edu.}
}

% Include the date command, but leave its argument blank.

\date{}

%%%%%%%%%%%%%%%%% END OF PREAMBLE %%%%%%%%%%%%%%%%

\begin{document}

% Double-space the manuscript.

\baselineskip24pt

% Make the title.

\maketitle

% Place your abstract within the special {sciabstract} environment.

\begin{sciabstract}
  This document presents a number of hints about how to set up your
  {\it Science\/} paper in \LaTeX\ .  We provide a template file,
  \texttt{scifile.tex}, that you can use to set up the \LaTeX\ source
  for your article.  An example of the style is the special
  \texttt{\{sciabstract\}} environment used to set up the abstract you
  see here.
\end{sciabstract}

% In setting up this template for *Science* papers, we've used both
% the \section* command and the \paragraph* command for topical
% divisions.  Which you use will of course depend on the type of paper
% you're writing.  Review Articles tend to have displayed headings, for
% which \section* is more appropriate; Research Articles, when they have
% formal topical divisions at all, tend to signal them with bold text
% that runs into the paragraph, for which \paragraph* is the right
% choice.  Either way, use the asterisk (*) modifier, as shown, to
% suppress numbering.

\section*{Introduction}

In this file, we present some tips and sample mark-up to assure your
\LaTeX\ file of the smoothest possible journey from review manuscript
to published {\it Science\/} paper.  We focus here particularly on
issues related to style files, citation, and math, tables, and
figures, as those tend to be the biggest sticking points.  Please use
the source file for this document, \texttt{scifile.tex}, as a template
for your manuscript, cutting and pasting your content into the file at
the appropriate places.

{\it Science\/}'s publication workflow relies on Microsoft Word97.  To
translate \LaTeX\ files into Word97, we use an intermediate MS-DOS
routine \cite{tth} that converts the \TeX\ source into HTML\@.  The
routine is generally robust, but it works best if the source document
is clean \LaTeX\ without a significant freight of local macros or
\texttt{.sty} files.  Use of the source file \texttt{scifile.tex} as a
template, and calling {\it only\/} the \texttt{.sty} and \texttt{.bst}
files specifically mentioned here, will generate a manuscript that
should be eminently reviewable, and yet will allow your paper to
proceed quickly into our production flow upon acceptance \cite{use2e}.

\section*{Formatting Citations}

Citations can be handled in one of three ways.  The most
straightforward (albeit labor-intensive) would be to hardwire your
citations into your \LaTeX\ source, as you would if you were using an
ordinary word processor.  Thus, your code might look something like
this:

\begin{quote}
\begin{verbatim}
However, this record of the solar nebula may have been
partly erased by the complex history of the meteorite
parent bodies, which includes collision-induced shock,
thermal metamorphism, and aqueous alteration
({\it 1, 2, 5--7\/}).
\end{verbatim}
\end{quote}

\noindent Compiled, the last two lines of the code above, of course, would give notecalls in {\it Science\/} style:

\begin{quote}
\ldots thermal metamorphism, and aqueous alteration ({\it 1, 2, 5--7\/}).
\end{quote}

Under the same logic, the author could set up his or her reference list as a simple enumeration,

\begin{quote}
\begin{verbatim}
{\bf References and Notes}

\begin{enumerate}
\item G. Gamow, {\it The Constitution of Atomic Nuclei
and Radioactivity\/} (Oxford Univ. Press, New York, 1931).
\item W. Heisenberg and W. Pauli, {\it Zeitschr.\ f.\
Physik\/} {\bf 56}, 1 (1929).
\end{enumerate}
\end{verbatim}
\end{quote}

\noindent yielding

\begin{quote}
{\bf References and Notes}

\begin{enumerate}
\item G. Gamow, {\it The Constitution of Atomic Nuclei and
Radioactivity\/} (Oxford Univ. Press, New York, 1931).
\item W. Heisenberg and W. Pauli, {\it Zeitschr.\ f.\ Physik} {\bf 56},
1 (1929).
\end{enumerate}
\end{quote}

That's not a solution that's likely to appeal to everyone, however ---
especially not to users of B{\small{IB}}\TeX\ \cite{inclme}.  If you
are a B{\small{IB}}\TeX\ user, we suggest that you use the
\texttt{Science.bst} bibliography style file and the
\texttt{scicite.sty} package, both of which we are downloadable from our author help site
(http://www.sciencemag.org/about/authors/prep/TeX_help/).  You can also
generate your reference lists by using the list environment
\texttt{\{thebibliography\}} at the end of your source document; here
again, you may find the \texttt{scicite.sty} file useful.

Whether you use B{\small{IB}}\TeX\ or \texttt{\{thebibliography\}}, be
very careful about how you set up your in-text reference calls and
notecalls.  In particular, observe the following requirements:

\begin{enumerate}
\item Please follow the style for references outlined at our author
  help site and embodied in recent issues of {\it Science}.  Each
  citation number should refer to a single reference; please do not
  concatenate several references under a single number.
\item Please cite your references and notes in text {\it only\/} using
  the standard \LaTeX\ \verb+\cite+ command, not another command
  driven by outside macros.
\item Please separate multiple citations within a single \verb+\cite+
  command using commas only; there should be {\it no space\/}
  between reference keynames.  That is, if you are citing two
  papers whose bibliography keys are \texttt{keyname1} and
  \texttt{keyname2}, the in-text cite should read
  \verb+\cite{keyname1,keyname2}+, {\it not\/}
  \verb+\cite{keyname1, keyname2}+.
\end{enumerate}

\noindent Failure to follow these guidelines could lead
to the omission of the references in an accepted paper when the source
file is translated to Word97 via HTML.

\section*{Handling Math, Tables, and Figures}

Following are a few things to keep in mind in coding equations,
tables, and figures for submission to {\it Science}.

\paragraph*{In-line math.}  The utility that we use for converting
from \LaTeX\ to HTML handles in-line math relatively well.  It is best
to avoid using built-up fractions in in-line equations, and going for
the more boring ``slash'' presentation whenever possible --- that is,
for \verb+$a/b$+ (which comes out as $a/b$) rather than
\verb+$\frac{a}{b}$+ (which compiles as $\frac{a}{b}$).  Likewise,
HTML isn't tooled to handle certain overaccented special characters
in-line; for $\hat{\alpha}$ (coded \verb+$\hat{\alpha}$+), for
example, the HTML translation code will return [\^{}$(\alpha)$].
Don't drive yourself crazy --- but if it's possible to avoid such
constructs, please do so.  Please do not code arrays or matrices as
in-line math; display them instead.  And please keep your coding as
\TeX-y as possible --- avoid using specialized math macro packages
like \texttt{amstex.sty}.

\paragraph*{Displayed math.} Our HTML converter sets up \TeX\
displayed equations using nested HTML tables.  That works well for an
HTML presentation, but Word97 chokes when it comes across a nested
table in an HTML file.  We surmount that problem by simply cutting the
displayed equations out of the HTML before it's imported into Word97,
and then replacing them in the Word document using either images or
equations generated by a Word equation editor.  Strictly speaking,
this procedure doesn't bear on how you should prepare your manuscript
--- although, for reasons best consigned to a note \cite{nattex}, we'd
prefer that you use native \TeX\ commands within displayed-math
environments, rather than \LaTeX\ sub-environments.

\paragraph*{Tables.}  The HTML converter that we use seems to handle
reasonably well simple tables generated using the \LaTeX\
\texttt{\{tabular\}} environment.  For very complicated tables, you
may want to consider generating them in a word processing program and
including them as a separate file.

\paragraph*{Figures.}  Figure callouts within the text should not be
in the form of \LaTeX\ references, but should simply be typed in ---
that is, \verb+(Fig. 1)+ rather than \verb+\ref{fig1}+.  For the
figures themselves, treatment can differ depending on whether the
manuscript is an initial submission or a final revision for acceptance
and publication.  For an initial submission and review copy, you can
use the \LaTeX\ \verb+{figure}+ environment and the
\verb+\includegraphics+ command to include your PostScript figures at
the end of the compiled PostScript file.  For the final revision,
however, the \verb+{figure}+ environment should {\it not\/} be used;
instead, the figure captions themselves should be typed in as regular
text at the end of the source file (an example is included here), and
the figures should be uploaded separately according to the Art
Department's instructions.

\section*{What to Send In}

What you should send to {\it Science\/} will depend on the stage your manuscript is in:

\begin{itemize}
\item {\bf Important:} If you're sending in the initial submission of
  your manuscript (that is, the copy for evaluation and peer review),
  please send in {\it only\/} a PostScript or PDF version of the
  compiled file (including figures).  Please do not send in the \TeX\
  source, \texttt{.sty}, \texttt{.bbl}, or other associated files with
  your initial submission.  (For more information, please see the
  instructions at our Web submission site,
  http://www.submit2science.org/ .)
\item When the time comes for you to send in your revised final
  manuscript (i.e., after peer review), we require that you include
  all source files and generated files in your upload.  Thus, if the
  name of your main source document is \texttt{ltxfile.tex}, you
  need to include:
\begin{itemize}
\item \texttt{ltxfile.tex}.
\item \texttt{ltxfile.aux}, the auxilliary file generated by the
  compilation.
\item A PostScript file (compiled using \texttt{dvips} or some other
  driver) of the \texttt{.dvi} file generated from
  \texttt{ltxfile.tex}, or a PDF file distilled from that
  PostScript.  You do not need to include the actual \texttt{.dvi}
  file in your upload.
\item From B{\small{IB}}\TeX\ users, your bibliography (\texttt{.bib})
  file, {\it and\/} the generated file \texttt{ltxfile.bbl} created
  when you run B{\small{IB}}\TeX.
\item Any additional \texttt{.sty} and \texttt{.bst} files called by
  the source code (though, for reasons noted earlier, we {\it
    strongly\/} discourage the use of such files beyond those
  mentioned in this document).
\end{itemize}
\end{itemize}

% Your references go at the end of the main text, and before the
% figures.  For this document we've used BibTeX, the .bib file
% scibib.bib, and the .bst file Science.bst.  The package scicite.sty
% was included to format the reference numbers according to *Science*
% style.

\bibliography{scibib}

\bibliographystyle{Science}

% Following is a new environment, {scilastnote}, that's defined in the
% preamble and that allows authors to add a reference at the end of the
% list that's not signaled in the text; such references are used in
% *Science* for acknowledgments of funding, help, etc.

\begin{scilastnote}
\item We've included in the template file \texttt{scifile.tex} a new
environment, \texttt{\{scilastnote\}}, that generates a numbered final
citation without a corresponding signal in the text.  This environment
can be used to generate a final numbered reference containing
acknowledgments, sources of funding, and the like, per {\it Science\/}
style.  Along those lines, we'd like to thank readers of this document
for their attention, and invite them to address any questions to
Stewart Wills, at swills@aaas.org.
\end{scilastnote}

% For your review copy (i.e., the file you initially send in for
% evaluation), you can use the {figure} environment and the
% \includegraphics command to stream your figures into the text, placing
% all figures at the end.  For the final, revised manuscript for
% acceptance and production, however, PostScript or other graphics
% should not be streamed into your compliled file.  Instead, set
% captions as simple paragraphs (with a \noindent tag), setting them
% off from the rest of the text with a \clearpage as shown  below, and
% submit figures as separate files according to the Art Department's
% instructions.

\clearpage

\noindent {\bf Fig. 1.} Please do not use figure environments to set
up your figures in the final (post-peer-review) draft, do not include graphics in your
source code, and do not cite figures in the text using \LaTeX\
\verb+\ref+ commands.  Instead, simply refer to the figure numbers in
the text per {\it Science\/} style, and include the list of captions at
the end of the document, coded as ordinary paragraphs as shown in the
\texttt{scifile.tex} template file.  Your actual figure files should
be submitted separately.

\end{document}

### 2016-01-10 docs/paper.tex
changed the template.

@@
-% Use only LaTeX2e, calling the article.cls class and 12-point type.
+\documentclass[twoside,11pt]{article}
 
-\documentclass[12pt]{article}
+% Any additional packages needed should be included after jmlr2e.
+% Note that jmlr2e.sty includes epsfig, amssymb, natbib and graphicx,
+% and defines many common macros, such as 'proof' and 'example'.
+%
+% It also sets the bibliographystyle to plainnat; for more information on
+% natbib citation styles, see the natbib documentation, a copy of which
+% is archived at http://www.jmlr.org/format/natbib.pdf
 
-% Users of the {thebibliography} environment or BibTeX should use the
-% scicite.sty package, downloadable from *Science* at
-% www.sciencemag.org/about/authors/prep/TeX_help/ .
-% This package should properly format in-text
-% reference calls and reference-list numbers.
+\usepackage{jmlr2e}
 
-\usepackage{scicite}
+% Definitions of handy macros can go here
 
-% Use times if you have the font installed; otherwise, comment out the
-% following line.
+\newcommand{\dataset}{{\cal D}}
+\newcommand{\fracpartial}[2]{\frac{\partial #1}{\partial  #2}}
 
-\usepackage{times}
+% Heading arguments are {volume}{year}{pages}{submitted}{published}{author-full-names}
 
-% The preamble here sets up a lot of new/revised commands and
-% environments.  It's annoying, but please do *not* try to strip these
-% out into a separate .sty file (which could lead to the loss of some
-% information when we convert the file to other formats).  Instead, keep
-% them in the preamble of your main LaTeX source file.
+\jmlrheading{1}{2000}{1-48}{4/00}{10/00}{Marina Meil\u{a} and Michael I. Jordan}
 
-% The following parameters seem to provide a reasonable page setup.
+% Short headings should be running head and authors last names
 
-\topmargin 0.0cm
-\oddsidemargin 0.2cm
-\textwidth 16cm
-\textheight 21cm
-\footskip 1.0cm
-
-%The next command sets up an environment for the abstract to your paper.
-
-\newenvironment{sciabstract}{%
-\begin{quote} \bf}
-{\end{quote}}
-
-% If your reference list includes text notes as well as references,
-% include the following line; otherwise, comment it out.
-
-\renewcommand\refname{References and Notes}
-
-% The following lines set up an environment for the last note in the
-% reference list, which commonly includes acknowledgments of funding,
-% help, etc.  It's intended for users of BibTeX or the {thebibliography}
-% environment.  Users who are hand-coding their references at the end
-% using a list environment such as {enumerate} can simply add another
-% item at the end, and it will be numbered automatically.
-
-\newcounter{lastnote}
-\newenvironment{scilastnote}{%
-\setcounter{lastnote}{\value{enumiv}}%
-\addtocounter{lastnote}{+1}%
-\begin{list}%
-{\arabic{lastnote}.}
-{\setlength{\leftmargin}{.22in}}
-{\setlength{\labelsep}{.5em}}}
-{\end{list}}
-
-% Include your paper's title here
-
-\title{A simple {\it Science\/} Template}
-
-% Place the author information here.  Please hand-code the contact
-% information and notecalls; do *not* use \footnote commands.  Let the
-% author contact information appear immediately below the author names
-% as shown.  We would also prefer that you don't change the type-size
-% settings shown here.
-
-\author
-{John Smith,$^{1\ast}$ Jane Doe,$^{1}$ Joe Scientist$^{2}$\\
-\\
-\normalsize{$^{1}$Department of Chemistry, University of Wherever,}\\
-\normalsize{An Unknown Address, Wherever, ST 00000, USA}\\
-\normalsize{$^{2}$Another Unknown Address, Palookaville, ST 99999, USA}\\
-\\
-\normalsize{$^\ast$To whom correspondence should be addressed; E-mail:  jsmith@wherever.edu.}
-}
-
-% Include the date command, but leave its argument blank.
-
-\date{}
-
-%%%%%%%%%%%%%%%%% END OF PREAMBLE %%%%%%%%%%%%%%%%
+\ShortHeadings{Learning with Mixtures of Trees}{Meil\u{a} and Jordan}
+\firstpageno{1}
 
@@
 
-% Double-space the manuscript.
+\title{Learning with Mixtures of Trees}
 
-\baselineskip24pt
+\author{\name Marina Meil\u{a} \email mmp@stat.washington.edu \\
+       \addr Department of Statistics\\
+       University of Washington\\
+       Seattle, WA 98195-4322, USA
+       \AND
+       \name Michael I.\ Jordan \email jordan@cs.berkeley.edu \\
+       \addr Division of Computer Science and Department of Statistics\\
+       University of California\\
+       Berkeley, CA 94720-1776, USA}
 
-% Make the title.
+\editor{Leslie Pack Kaelbling}
 
-\maketitle
+\maketit
 
-% Place your abstract within the special {sciabstract} environment.
+\begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
+This paper describes the mixtures-of-trees model, a probabilistic 
+model for discrete multidimensional domains.  Mixtures-of-trees 
+generalize the probabilistic trees of \citet{chow:68}
+in a different and complementary direction to that of Bayesian networks.
+We present efficient algorithms for learning mixtures-of-trees 
+models in maximum likelihood and Bayesian frameworks. 
+We also discuss additional efficiencies that can be
+obtained when data are ``sparse,'' and we present data 
+structures and algorithms that exploit such sparseness.
+Experimental results demonstrate the performance of the 
+model for both density estimation and classification. 
+We also discuss the sense in which tree-based classifiers
+perform an implicit form of feature selection, and demonstrate
+a resulting insensitivity to irrelevant attributes.
+\end{abstract}
 
-\begin{sciabstract}
-  This document presents a number of hints about how to set up your
-  {\it Science\/} paper in \LaTeX\ .  We provide a template file,
-  \texttt{scifile.tex}, that you can use to set up the \LaTeX\ source
-  for your article.  An example of the style is the special
-  \texttt{\{sciabstract\}} environment used to set up the abstract you
-  see here.
-\end{sciabstract}
+\begin{keywords}
+  Bayesian Networks, Mixture Models, Chow-Liu Trees
+\end{keywords}
 
-% In setting up this template for *Science* papers, we've used both
-% the \section* command and the \paragraph* command for topical
-% divisions.  Which you use will of course depend on the type of paper
-% you're writing.  Review Articles tend to have displayed headings, for
-% which \section* is more appropriate; Research Articles, when they have
-% formal topical divisions at all, tend to signal them with bold text
-% that runs into the paragraph, for which \paragraph* is the right
-% choice.  Either way, use the asterisk (*) modifier, as shown, to
-% suppress numbering.
+\section{Introduction}
 
-\section*{Introduction}
+Probabilistic inference has become a core technology in AI,
+largely due to developments in graph-theoretic methods for the 
+representation and manipulation of complex probability 
+distributions~\citep{pearl:88}.  Whether in their guise as 
+directed graphs (Bayesian networks) or as undirected graphs (Markov 
+random fields), \emph{probabilistic graphical models} have a number 
+of virtues as representations of uncertainty and as inference engines.  
+Graphical models allow a separation between qualitative, structural
+aspects of uncertain knowledge and the quantitative, parametric aspects 
+of uncertainty...\\
 
-In this file, we present some tips and sample mark-up to assure your
-\LaTeX\ file of the smoothest possible journey from review manuscript
-to published {\it Science\/} paper.  We focus here particularly on
-issues related to style files, citation, and math, tables, and
-figures, as those tend to be the biggest sticking points.  Please use
-the source file for this document, \texttt{scifile.tex}, as a template
-for your manuscript, cutting and pasting your content into the file at
-the appropriate places.
+{\noindent \em Remainder omitted in this sample. See http://www.jmlr.org/papers/ for full paper.}
 
-{\it Science\/}'s publication workflow relies on Microsoft Word97.  To
-translate \LaTeX\ files into Word97, we use an intermediate MS-DOS
-routine \cite{tth} that converts the \TeX\ source into HTML\@.  The
-routine is generally robust, but it works best if the source document
-is clean \LaTeX\ without a significant freight of local macros or
-\texttt{.sty} files.  Use of the source file \texttt{scifile.tex} as a
-template, and calling {\it only\/} the \texttt{.sty} and \texttt{.bst}
-files specifically mentioned here, will generate a manuscript that
-should be eminently reviewable, and yet will allow your paper to
-proceed quickly into our production flow upon acceptance \cite{use2e}.
+% Acknowledgements should go at the end, before appendices and references
 
-\section*{Formatting Citations}
+\acks{We would like to acknowledge support for this project
+from the National Science Foundation (NSF grant IIS-9988642)
+and the Multidisciplinary Research Program of the Department
+of Defense (MURI N00014-00-1-0637). }
 
-Citations can be handled in one of three ways.  The most
-straightforward (albeit labor-intensive) would be to hardwire your
-citations into your \LaTeX\ source, as you would if you were using an
-ordinary word processor.  Thus, your code might look something like
-this:
+% Manual newpage inserted to improve layout of sample file - not
+% needed in general before appendices/bibliography.
 
-\begin{quote}
-\begin{verbatim}
-However, this record of the solar nebula may have been
-partly erased by the complex history of the meteorite
-parent bodies, which includes collision-induced shock,
-thermal metamorphism, and aqueous alteration
-({\it 1, 2, 5--7\/}).
-\end{verbatim}
-\end{quote}
+\newpage
 
-\noindent Compiled, the last two lines of the code above, of course, would give notecalls in {\it Science\/} style:
+\appendix
+\section*{Appendix A.}
+\label{app:theorem}
 
-\begin{quote}
-\ldots thermal metamorphism, and aqueous alteration ({\it 1, 2, 5--7\/}).
-\end{quote}
+% Note: in this sample, the section number is hard-coded in. Following
+% proper LaTeX conventions, it should properly be coded as a reference:
 
-Under the same logic, the author could set up his or her reference list as a simple enumeration,
+%In this appendix we prove the following theorem from
+%Section~\ref{sec:textree-generalization}:
 
-\begin{quote}
-\begin{verbatim}
-{\bf References and Notes}
+In this appendix we prove the following theorem from
+Section~6.2:
 
-\begin{enumerate}
-\item G. Gamow, {\it The Constitution of Atomic Nuclei
-and Radioactivity\/} (Oxford Univ. Press, New York, 1931).
-\item W. Heisenberg and W. Pauli, {\it Zeitschr.\ f.\
-Physik\/} {\bf 56}, 1 (1929).
-\end{enumerate}
-\end{verbatim}
-\end{quote}
+\noindent
+{\bf Theorem} {\it Let $u,v,w$ be discrete variables such that $v, w$ do
+not co-occur with $u$ (i.e., $u\neq0\;\Rightarrow \;v=w=0$ in a given
+dataset $\dataset$). Let $N_{v0},N_{w0}$ be the number of data points for
+which $v=0, w=0$ respectively, and let $I_{uv},I_{uw}$ be the
+respective empirical mutual information values based on the sample
+$\dataset$. Then
+\[
+	N_{v0} \;>\; N_{w0}\;\;\Rightarrow\;\;I_{uv} \;\leq\;I_{uw}
+\]
+with equality only if $u$ is identically 0.} \hfill\BlackBox
 
-\noindent yielding
+\noindent
+{\bf Proof}. We use the notation:
+\[
+P_v(i) \;=\;\frac{N_v^i}{N},\;\;\;i \neq 0;\;\;\;
+P_{v0}\;\equiv\;P_v(0)\; = \;1 - \sum_{i\neq 0}P_v(i).
+\]
+These values represent the (empirical) probabilities of $v$
+taking value $i\neq 0$ and 0 respectively.  Entropies will be denoted
+by $H$. We aim to show that $\fracpartial{I_{uv}}{P_{v0}} < 0$....\\
 
-\begin{quote}
-{\bf References and Notes}
+{\noindent \em Remainder omitted in this sample. See http://www.jmlr.org/papers/ for full paper.}
 
-\begin{enumerate}
-\item G. Gamow, {\it The Constitution of Atomic Nuclei and
-Radioactivity\/} (Oxford Univ. Press, New York, 1931).
-\item W. Heisenberg and W. Pauli, {\it Zeitschr.\ f.\ Physik} {\bf 56},
-1 (1929).
-\end{enumerate}
-\end{quote}
-
-That's not a solution that's likely to appeal to everyone, however ---
-especially not to users of B{\small{IB}}\TeX\ \cite{inclme}.  If you
-are a B{\small{IB}}\TeX\ user, we suggest that you use the
-\texttt{Science.bst} bibliography style file and the
-\texttt{scicite.sty} package, both of which we are downloadable from our author help site
-(http://www.sciencemag.org/about/authors/prep/TeX_help/).  You can also
-generate your reference lists by using the list environment
-\texttt{\{thebibliography\}} at the end of your source document; here
-again, you may find the \texttt{scicite.sty} file useful.
-
-Whether you use B{\small{IB}}\TeX\ or \texttt{\{thebibliography\}}, be
-very careful about how you set up your in-text reference calls and
-notecalls.  In particular, observe the following requirements:
-
-\begin{enumerate}
-\item Please follow the style for references outlined at our author
-  help site and embodied in recent issues of {\it Science}.  Each
-  citation number should refer to a single reference; please do not
-  concatenate several references under a single number.
-\item Please cite your references and notes in text {\it only\/} using
-  the standard \LaTeX\ \verb+\cite+ command, not another command
-  driven by outside macros.
-\item Please separate multiple citations within a single \verb+\cite+
-  command using commas only; there should be {\it no space\/}
-  between reference keynames.  That is, if you are citing two
-  papers whose bibliography keys are \texttt{keyname1} and
-  \texttt{keyname2}, the in-text cite should read
-  \verb+\cite{keyname1,keyname2}+, {\it not\/}
-  \verb+\cite{keyname1, keyname2}+.
-\end{enumerate}
-
-\noindent Failure to follow these guidelines could lead
-to the omission of the references in an accepted paper when the source
-file is translated to Word97 via HTML.
-
-\section*{Handling Math, Tables, and Figures}
-
-Following are a few things to keep in mind in coding equations,
-tables, and figures for submission to {\it Science}.
-
-\paragraph*{In-line math.}  The utility that we use for converting
-from \LaTeX\ to HTML handles in-line math relatively well.  It is best
-to avoid using built-up fractions in in-line equations, and going for
-the more boring ``slash'' presentation whenever possible --- that is,
-for \verb+$a/b$+ (which comes out as $a/b$) rather than
-\verb+$\frac{a}{b}$+ (which compiles as $\frac{a}{b}$).  Likewise,
-HTML isn't tooled to handle certain overaccented special characters
-in-line; for $\hat{\alpha}$ (coded \verb+$\hat{\alpha}$+), for
-example, the HTML translation code will return [\^{}$(\alpha)$].
-Don't drive yourself crazy --- but if it's possible to avoid such
-constructs, please do so.  Please do not code arrays or matrices as
-in-line math; display them instead.  And please keep your coding as
-\TeX-y as possible --- avoid using specialized math macro packages
-like \texttt{amstex.sty}.
-
-\paragraph*{Displayed math.} Our HTML converter sets up \TeX\
-displayed equations using nested HTML tables.  That works well for an
-HTML presentation, but Word97 chokes when it comes across a nested
-table in an HTML file.  We surmount that problem by simply cutting the
-displayed equations out of the HTML before it's imported into Word97,
-and then replacing them in the Word document using either images or
-equations generated by a Word equation editor.  Strictly speaking,
-this procedure doesn't bear on how you should prepare your manuscript
---- although, for reasons best consigned to a note \cite{nattex}, we'd
-prefer that you use native \TeX\ commands within displayed-math
-environments, rather than \LaTeX\ sub-environments.
-
-\paragraph*{Tables.}  The HTML converter that we use seems to handle
-reasonably well simple tables generated using the \LaTeX\
-\texttt{\{tabular\}} environment.  For very complicated tables, you
-may want to consider generating them in a word processing program and
-including them as a separate file.
-
-\paragraph*{Figures.}  Figure callouts within the text should not be
-in the form of \LaTeX\ references, but should simply be typed in ---
-that is, \verb+(Fig. 1)+ rather than \verb+\ref{fig1}+.  For the
-figures themselves, treatment can differ depending on whether the
-manuscript is an initial submission or a final revision for acceptance
-and publication.  For an initial submission and review copy, you can
-use the \LaTeX\ \verb+{figure}+ environment and the
-\verb+\includegraphics+ command to include your PostScript figures at
-the end of the compiled PostScript file.  For the final revision,
-however, the \verb+{figure}+ environment should {\it not\/} be used;
-instead, the figure captions themselves should be typed in as regular
-text at the end of the source file (an example is included here), and
-the figures should be uploaded separately according to the Art
-Department's instructions.
-
-\section*{What to Send In}
-
-What you should send to {\it Science\/} will depend on the stage your manuscript is in:
-
-\begin{itemize}
-\item {\bf Important:} If you're sending in the initial submission of
-  your manuscript (that is, the copy for evaluation and peer review),
-  please send in {\it only\/} a PostScript or PDF version of the
-  compiled file (including figures).  Please do not send in the \TeX\
-  source, \texttt{.sty}, \texttt{.bbl}, or other associated files with
-  your initial submission.  (For more information, please see the
-  instructions at our Web submission site,
-  http://www.submit2science.org/ .)
-\item When the time comes for you to send in your revised final
-  manuscript (i.e., after peer review), we require that you include
-  all source files and generated files in your upload.  Thus, if the
-  name of your main source document is \texttt{ltxfile.tex}, you
-  need to include:
-\begin{itemize}
-\item \texttt{ltxfile.tex}.
-\item \texttt{ltxfile.aux}, the auxilliary file generated by the
-  compilation.
-\item A PostScript file (compiled using \texttt{dvips} or some other
-  driver) of the \texttt{.dvi} file generated from
-  \texttt{ltxfile.tex}, or a PDF file distilled from that
-  PostScript.  You do not need to include the actual \texttt{.dvi}
-  file in your upload.
-\item From B{\small{IB}}\TeX\ users, your bibliography (\texttt{.bib})
-  file, {\it and\/} the generated file \texttt{ltxfile.bbl} created
-  when you run B{\small{IB}}\TeX.
-\item Any additional \texttt{.sty} and \texttt{.bst} files called by
-  the source code (though, for reasons noted earlier, we {\it
-    strongly\/} discourage the use of such files beyond those
-  mentioned in this document).
-\end{itemize}
-\end{itemize}
-
-% Your references go at the end of the main text, and before the
-% figures.  For this document we've used BibTeX, the .bib file
-% scibib.bib, and the .bst file Science.bst.  The package scicite.sty
-% was included to format the reference numbers according to *Science*
-% style.
-
-\bibliography{scibib}
-
-\bibliographystyle{Science}
-
-% Following is a new environment, {scilastnote}, that's defined in the
-% preamble and that allows authors to add a reference at the end of the
-% list that's not signaled in the text; such references are used in
-% *Science* for acknowledgments of funding, help, etc.
-
-\begin{scilastnote}
-\item We've included in the template file \texttt{scifile.tex} a new
-environment, \texttt{\{scilastnote\}}, that generates a numbered final
-citation without a corresponding signal in the text.  This environment
-can be used to generate a final numbered reference containing
-acknowledgments, sources of funding, and the like, per {\it Science\/}
-style.  Along those lines, we'd like to thank readers of this document
-for their attention, and invite them to address any questions to
-Stewart Wills, at swills@aaas.org.
-\end{scilastnote}
-
-% For your review copy (i.e., the file you initially send in for
-% evaluation), you can use the {figure} environment and the
-% \includegraphics command to stream your figures into the text, placing
-% all figures at the end.  For the final, revised manuscript for
-% acceptance and production, however, PostScript or other graphics
-% should not be streamed into your compliled file.  Instead, set
-% captions as simple paragraphs (with a \noindent tag), setting them
-% off from the rest of the text with a \clearpage as shown  below, and
-% submit figures as separate files according to the Art Department's
-% instructions.
-
-\clearpage
-
-\noindent {\bf Fig. 1.} Please do not use figure environments to set
-up your figures in the final (post-peer-review) draft, do not include graphics in your
-source code, and do not cite figures in the text using \LaTeX\
-\verb+\ref+ commands.  Instead, simply refer to the figure numbers in
-the text per {\it Science\/} style, and include the list of captions at
-the end of the document, coded as ordinary paragraphs as shown in the
-\texttt{scifile.tex} template file.  Your actual figure files should
-be submitted separately.
+\vskip 0.2in
+\bibliography{sample}
 

### 2016-01-12 Sources.py
fixed mongodb import

@@ -1,11 +1,10 @@
 ## count tweet sources
 import operator
 
-from data import MongoDB
+from data.MongoDB import db
 from helpers import Dictrement
-from settings import mongod_config
 
-mongodb = MongoDB(mongod_config)
+mongodb = db
 docs = mongodb.tweets_collection.find()
 source_dictrement = Dictrement()
 count = 0

### 2016-01-12 data/Filters.py
imported db for filters

@@ -1,9 +1,10 @@
 import settings
+from data.MongoDB import db
 
 
 class Filters:
-    def __init__(self, mongodb):
-        self.mongodb = mongodb
+    def __init__(self):
+        self.mongodb = db
         self.source_whitelist = Filters.get_source_whitelist()
 
     def get_location_filter_query(self):

### 2016-01-12 sklearn_comparison.py
added binary classification and user history configuration parameters to results.

@@ -96,6 +96,7 @@ def main(classifier=None):
 def run_classifier_with_id(classifier_id):
     executor = ClassifierExecutor(classifiers[classifier_id], binary_classification=binary_classification)
     result = {"classifier": classifier_names[classifier_id], "classifier_id": classifier_id,
+              "binary_classification": binary_classification, "include_user_history": include_user_history,
               "started_at": datetime.now(), "meta": instance_meta}
     execution.write_progress(result)
     try:

### 2016-01-12 docs/paper.tex
initial version of the paper

@@
 \documentclass[twoside,11pt]{article}
+
+% !!!!!
+As a rule, use past tense to describe events that have happened.
+Such events include procedures that you have conducted and results that you observed.
+Use present tense to describe generally accepted facts.
+!!!!!
 
@@
 \usepackage{jmlr2e}
-
+\usepackage{amssymb} %maths
+\usepackage{amsmath} %maths
 % Definitions of handy macros can go here
@@
 
-\jmlrheading{1}{2000}{1-48}{4/00}{10/00}{Marina Meil\u{a} and Michael I. Jordan}
+% \jmlrheading{1}{2000}{1-48}{4/00}{10/00}{Marina Meil\u{a} and Michael I. Jordan}
 
@@
 
-\ShortHeadings{Learning with Mixtures of Trees}{Meil\u{a} and Jordan}
+\ShortHeadings{Location Classification on Tweets}{Erdi \c{C}all{\i}}
 \firstpageno{1}
@@
 
-\title{Learning with Mixtures of Trees}
+\title{Location Classification on Tweets}
+\author{\name Erdi \c{C}all{\i} \\ \email erdicalli@gmail.com \\ s4600673}
 
-\author{\name Marina Meil\u{a} \email mmp@stat.washington.edu \\
-       \addr Department of Statistics\\
-       University of Washington\\
-       Seattle, WA 98195-4322, USA
-       \AND
-       \name Michael I.\ Jordan \email jordan@cs.berkeley.edu \\
-       \addr Division of Computer Science and Department of Statistics\\
-       University of California\\
-       Berkeley, CA 94720-1776, USA}
+\maketitle
 
-\editor{Leslie Pack Kaelbling}
-
-\maketit
-
-\begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
-This paper describes the mixtures-of-trees model, a probabilistic 
-model for discrete multidimensional domains.  Mixtures-of-trees 
-generalize the probabilistic trees of \citet{chow:68}
-in a different and complementary direction to that of Bayesian networks.
-We present efficient algorithms for learning mixtures-of-trees 
-models in maximum likelihood and Bayesian frameworks. 
-We also discuss additional efficiencies that can be
-obtained when data are ``sparse,'' and we present data 
-structures and algorithms that exploit such sparseness.
-Experimental results demonstrate the performance of the 
-model for both density estimation and classification. 
-We also discuss the sense in which tree-based classifiers
-perform an implicit form of feature selection, and demonstrate
-a resulting insensitivity to irrelevant attributes.
+\begin{abstract}%
+this is the last thing.
 \end{abstract}
@@
 \begin{keywords}
-  Bayesian Networks, Mixture Models, Chow-Liu Trees
+Supervised Learning, Classification, Twitter, Geolocation
 \end{keywords}
@@
 
-Probabilistic inference has become a core technology in AI,
-largely due to developments in graph-theoretic methods for the 
-representation and manipulation of complex probability 
-distributions~\citep{pearl:88}.  Whether in their guise as 
-directed graphs (Bayesian networks) or as undirected graphs (Markov 
-random fields), \emph{probabilistic graphical models} have a number 
-of virtues as representations of uncertainty and as inference engines.  
-Graphical models allow a separation between qualitative, structural
-aspects of uncertain knowledge and the quantitative, parametric aspects 
-of uncertainty...\\
+Proliferation of microblogging platforms, such as Twitter, enabled companies to learn valuable information about their products, customers and businesses.
+Twitter, introduced the option to include location information on tweets(geotagging) in 2009\footnote{https://blog.twitter.com/2009/location-location-location}.
+Since then, many applications(i.e Foursquare) and users started embedding this information to enrich the tweet content.
+But this information is not always shared by users.
+Using geotagged tweets to train classification algorithms, it may be possible to infer tweet locations.
 
-{\noindent \em Remainder omitted in this sample. See http://www.jmlr.org/papers/ for full paper.}
+Using sentimental analysis\footnote{Twitter as a Corpus for Sentiment Analysis and Opinion Mining.
+A Pak, P Paroubek - LREC, 2010}, a company can learn if its customers are happy with their products or a political figure can get feedback from his/her voters.
+The possibilities are endless.
+Incorporating this information with geolocation may be valuable in lots of situations for politicians, businesses and other parties.
+
+% TODO: REWRITE THIS PART AFTER CHECKING OTHER RESEARCH!
+This problem is first researched in a paper called \textit{You are where you tweet: a content-based approach to geo-locating twitter users}\footnote{http://dl.acm.org/citation.cfm?id=1871535}.
+Then improved with different studies such as \textit{Broadly Improving User Classification via
+Communication-Based Name and Location Clustering on Twitter}\footnote{http://www.aclweb.org/old\_anthology/N/N13/N13-1121.pdf}.
+These studies got accuracy up to 55 percent, not only using the tweet text, but also introducing other factors such as user behaviour.
+
+% TODO: check your highest recall rate
+Comparing different Machine Learning algorithms implemented in Scikit Learn\footnote{http://scikit-learn.org/}, we have tried to find the best algorithm to approach this problem.
+Introducing different configurations and optimisations, we have achieved a recall rate up to 60\% in binary classification.
+
+\section{Related Work}
+
+\section{Data Collection and Analysis}
+Using Twitter's sample status streaming api\footnote{https://dev.twitter.com/streaming/reference/get/statuses/sample}, we have collected data.
+This api returns approximately 1\% of the public tweets from all around the world.
+We have filtered this data to reduce the problem space to only location classification.
+Our filter selects only the geotagged English tweets, sent within the United States.
+Running this collector for 1 month, we have collected a dataset consisting of 33112 individual tweets, each from a unique user.
+We have also collected a sample of 40 tweets from those users, if their timelines are public, to enrich the dataset.
+
+Upon investigating this dataset, we have realised that there are a lot of low quality, automated tweets, coming from 886 different tweet sources(devices or applications that a tweet has been sent from).
+To remove these sources, we have created a whitelist of most used 20 sources that selects applications which real users use to tweet from.
+This reduced the amount of data by around 50\%, to 17040 individual geotagged tweets.
+
+Investigating the locations the tweets has been sent, we have seen that there are 3306 different locations(location full name in this case) that tweets have been geotagged with.
+
+One problem with the locations is the granularity.
+A location can appear as a state(New York, US), a city(New York, NY) or a neighbourhood(Manhattan, NY).
+A selection of 8 top locations, not intersecting each other, is selected from the ones containing the most tweets.
+% TODO: add some figure here, table or histogram of location counts
+
+\section{Experiments}
+% TODO: bag of words reference
+
+\subsection{Empirical Bayes}
+% TODO empirical prior reference
+% TODO twokenize footnote
+In this experiment we have tokenised each tweet using the $twokenize$ module, to convert them to a $bag\ of\ words$, calculate the probability of each "token given location" and probability of each location to find the maximum probability among locations.
+\begin{equation*}
+\begin{split}
+\mathbf{T} &= Tokens \\
+L &= Location \\
+p(L|\mathbf{T}) &= \frac{p(\mathbf{T} | L)p(L)}{p(T)}
+\end{split}
+\end{equation*}
+With likelihood $p(\mathbf{T} | L)$ and prior $p(\mathbf{L})$. For the prior, instead of assuming a distribution, we have generated an empirical prior and applied MAP estimate to the posterior;
+\begin{equation*}
+\hat{L} = \arg\max_L\{p(\mathbf{T} | L) P(L)\}
+\end{equation*}
+where;
+\begin{equation*}
+\begin{split}
+p(\mathbf{T} | L) &= \prod_i{p(t_i|L)}\\
+\end{split}
+\end{equation*}
+Empirical prior $p(L)$ is referring to the probability of a location L in the training data.
+
+This experiment have been tested for 2 different configurations.
+In the first configuration, the collection of sample tweets and geotagged tweet belonging to an individual user are accepted as one document, assuming the same location as geotagged tweet.
+In the second configuration, each sample tweet of an individual are accepted as separate documents with same assumption.
+
+The problem with this experiment was, if a token($t_x$) didn't appear in the training dataset, tweets containing this token gots a probability of 0.
+To avoid this problem we have ignored those tokens in the MAP estimate.
+
+%TODO: include results
+\subsection{Scikit Learn}
+This experiment compares the classification methods implemented in Scikit Learn(sklearn)(v0.17) library with different configurations.
 
@@
 
-\acks{We would like to acknowledge support for this project
-from the National Science Foundation (NSF grant IIS-9988642)
-and the Multidisciplinary Research Program of the Department
-of Defense (MURI N00014-00-1-0637). }
+% \acks{We would like to acknowledge support for this project
+% from the National Science Foundation (NSF grant IIS-9988642)
+% and the Multidisciplinary Research Program of the Department
+% of Defense (MURI N00014-00-1-0637). }
 

### 2016-01-12 analysis/SKLearn.py
made ngram configurable.

@@ -29,7 +29,8 @@ class ClassifierExecutor:
 
 
 class DataVectorizer:
-    def __init__(self, ngram_range=(1, 2), binary_classification=False, include_user_history=True):
+    def __init__(self, ngram=2, binary_classification=False, include_user_history=True):
+        ngram_range = (1, ngram)
         self.vectorizer = CountVectorizer(min_df=1, ngram_range=ngram_range)
         self.tfidf_transformer = TfidfTransformer()
         self.binary_classification = binary_classification
@@ -124,17 +125,19 @@ class DataVectorizer:
 
 
 class Corpus:
-    def __init__(self, binary_classification=False, include_user_history=True):
+    def __init__(self, binary_classification=False, include_user_history=True, ngram=2):
         self.underlying = None
         self.initialized = False
         self.binary_classification = binary_classification
         self.include_user_history = include_user_history
+        self.ngram = ngram
 
     def get(self):
         if not self.initialized:
             data = Data(include_user_history=self.include_user_history)
             vectorizer = DataVectorizer(binary_classification=self.binary_classification,
-                                        include_user_history=self.include_user_history)
+                                        include_user_history=self.include_user_history,
+                                        ngram=self.ngram)
             self.underlying = vectorizer.convert(data.get_training_data(), data.get_test_data())
             self.initialized = True
         return self.underlying

### 2016-01-12 sklearn_comparison.py

@@ -77,9 +77,10 @@ classifier_names = [
 
 binary_classification = False
 include_user_history = False
+ngram = 2
 execution = Execution()
 instance_meta = {}
-corpus = Corpus(binary_classification=binary_classification, include_user_history=include_user_history)
+corpus = Corpus(ngram=ngram, binary_classification=binary_classification, include_user_history=include_user_history)
 
 
 def main(classifier=None):
@@ -97,6 +98,7 @@ def run_classifier_with_id(classifier_id):
     executor = ClassifierExecutor(classifiers[classifier_id], binary_classification=binary_classification)
     result = {"classifier": classifier_names[classifier_id], "classifier_id": classifier_id,
               "binary_classification": binary_classification, "include_user_history": include_user_history,
+              "ngram": ngram,
               "started_at": datetime.now(), "meta": instance_meta}
     execution.write_progress(result)
     try:

### 2016-01-12 analysis/SKLearn.py
removed unnecessary prints

@@ -39,10 +39,6 @@ class DataVectorizer:
     def convert(self, training_docs, test_docs):
         training_corpus = self.normalise(self.__create_corpus__(training_docs))
         test_corpus = self.normalise(self.__create_corpus__(test_docs))
-        print sum(training_corpus["document_labels"])
-        print len(training_corpus["document_labels"])
-        print sum(test_corpus["document_labels"])
-        print len(test_corpus["document_labels"])
         training_corpus['tfidfs'] = self.tfidf_transformer.fit_transform(
                 self.vectorizer.fit_transform(training_corpus['documents']))
         test_corpus['tfidfs'] = self.tfidf_transformer.transform(self.vectorizer.transform(test_corpus['documents']))

### 2016-01-12 sklearn_comparison.py
removed no-good algorithms

@@ -14,10 +14,6 @@ from analysis.SKLearn import ClassifierExecutor, Corpus
 from data.Execution import Execution
 
 classifiers = [
-    LinearRegression(),
-    RidgeCV(alphas=[.1, .5, 1, 5, 10]),
-    LassoCV(),
-    ElasticNetCV(),
     LogisticRegressionCV(),
     SGDClassifier(loss="hinge"),
     SGDClassifier(loss="log"),
@@ -36,8 +32,6 @@ classifiers = [
     LinearSVC(),
     KNeighborsClassifier(n_neighbors=8, weights="uniform"),
     KNeighborsClassifier(n_neighbors=8, weights="distance"),
-    RadiusNeighborsClassifier(weights="uniform"),
-    RadiusNeighborsClassifier(weights="distance"),
     MultinomialNB(),
     BernoulliNB(),
     DecisionTreeClassifier(),
@@ -45,10 +39,6 @@ classifiers = [
 ]
 
 classifier_names = [
-    'LinearRegression()',
-    'RidgeCV(alphas=[.1, .5, 1, 5, 10])',
-    'LassoCV()',
-    'ElasticNetCV()',
     'LogisticRegressionCV()',
     'SGDClassifier(loss="hinge")',
     'SGDClassifier(loss="log")',
@@ -67,8 +57,6 @@ classifier_names = [
     'LinearSVC()',
     'KNeighborsClassifier(n_neighbors=8, weights="uniform")',
     'KNeighborsClassifier(n_neighbors=8, weights="distance")',
-    'RadiusNeighborsClassifier(weights="uniform")',
-    'RadiusNeighborsClassifier(weights="distance")',
     'MultinomialNB()',
     'BernoulliNB()',
     'DecisionTreeClassifier()',

### 2016-01-12 sklearn_comparison.py
moved main into a class.

@@ -2,10 +2,9 @@ import sys
 from datetime import datetime
 
 from sklearn.ensemble import AdaBoostClassifier
-from sklearn.linear_model import LogisticRegressionCV, SGDClassifier, RidgeCV, LinearRegression, LassoCV, ElasticNetCV, \
-    Perceptron, PassiveAggressiveClassifier
+from sklearn.linear_model import LogisticRegressionCV, SGDClassifier, Perceptron, PassiveAggressiveClassifier
 from sklearn.naive_bayes import MultinomialNB, BernoulliNB
-from sklearn.neighbors import KNeighborsClassifier, RadiusNeighborsClassifier
+from sklearn.neighbors import KNeighborsClassifier
 from sklearn.svm import SVC, LinearSVC
 from sklearn.tree import DecisionTreeClassifier
 
@@ -79,60 +78,64 @@ execution = Execution()
 instance_meta = {}
 
 
-def create_corpus(configuration):
-    return Corpus(binary_classification=configuration[0], include_user_history=configuration[1],
-                  ngram=configuration[2])
+class Main:
+    def __init__(self):
+        self.instance_meta = {}
 
+    @staticmethod
+    def create_corpus(configuration):
+        return Corpus(binary_classification=configuration[0], include_user_history=configuration[1],
+                      ngram=configuration[2])
 
-def main(classifier=None, configuration_id=0):
-    if classifier is None:
-        for index in range(0, len(classifiers)):
-            run_classifier_with_id(index, configuration_id)
-    elif classifier == "all-gcloud":
-        super.instance_meta = gcloud.get_metadata()
-        run_after_progress()
-    else:
-        run_classifier_with_id(int(classifier), configuration_id)
+    def start(self, classifier=None, configuration_id=0):
+        if classifier is None:
+            for index in range(0, len(classifiers)):
+                self.run_classifier_with_id(index, configuration_id)
+        elif classifier == "all-gcloud":
+            # self.instance_meta = gcloud.get_metadata()
+            self.run_after_progress()
+        else:
+            self.run_classifier_with_id(int(classifier), configuration_id)
 
+    def run_classifier_with_id(self, classifier_id, configuration_id):
+        configuration = configurations[configuration_id]
+        result = {"classifier": classifier_names[classifier_id], "classifier_id": classifier_id,
+                  "configuration_id": configuration_id, "binary_classification": configuration[0],
+                  "include_user_history": configuration[1], "ngram": configuration[2], "started_at": datetime.now(),
[…]

### 2016-01-12 sklearn_comparison.py
re enabled gcloud-meta

@@ -92,7 +92,7 @@ class Main:
             for index in range(0, len(classifiers)):
                 self.run_classifier_with_id(index, configuration_id)
         elif classifier == "all-gcloud":
-            # self.instance_meta = gcloud.get_metadata()
+            self.instance_meta = gcloud.get_metadata()
             self.run_after_progress()
         else:
             self.run_classifier_with_id(int(classifier), configuration_id)

### 2016-01-12 sklearn_comparison.py
collusion protection

@@ -1,5 +1,7 @@
+import random
 import sys
 from datetime import datetime
+from time import sleep
 
 from sklearn.ensemble import AdaBoostClassifier
 from sklearn.linear_model import LogisticRegressionCV, SGDClassifier, Perceptron, PassiveAggressiveClassifier
@@ -92,6 +94,7 @@ class Main:
             for index in range(0, len(classifiers)):
                 self.run_classifier_with_id(index, configuration_id)
         elif classifier == "all-gcloud":
+            sleep(random.random() * 10)  # instead of locking tables, this is much easier to avoid collusion
             self.instance_meta = gcloud.get_metadata()
             self.run_after_progress()
         else:

### 2016-01-12 sklearn_comparison.py
removed out of instance/scope elements from executor

@@ -76,13 +76,11 @@ configurations = [
     (True, True, 2),
 ]
 
-execution = Execution()
-instance_meta = {}
-
 
 class Main:
     def __init__(self):
         self.instance_meta = {}
+        self.execution = Execution()
 
     @staticmethod
     def create_corpus(configuration):
@@ -105,8 +103,8 @@ class Main:
         result = {"classifier": classifier_names[classifier_id], "classifier_id": classifier_id,
                   "configuration_id": configuration_id, "binary_classification": configuration[0],
                   "include_user_history": configuration[1], "ngram": configuration[2], "started_at": datetime.now(),
-                  "meta": instance_meta}
-        execution.write_progress(result)
+                  "meta": self.instance_meta}
+        self.execution.write_progress(result)
         corpus = self.create_corpus(configuration)
         executor = ClassifierExecutor(classifiers[classifier_id], binary_classification=configuration[0])
         try:
@@ -117,10 +115,10 @@ class Main:
             result['exception'] = str(sys.exc_info())
         result['ended_at'] = datetime.now()
         result['execution_time'] = str(result['ended_at'] - result['started_at'])
-        execution.write_execution_result(result)
+        self.execution.write_execution_result(result)
 
     def run_after_progress(self):
-        progress = execution.get_last_progress()
+        progress = self.execution.get_last_progress()
         if progress is None:
             self.run_classifier_with_id(0, 0)
             return self.run_after_progress()

### 2016-01-13 sklearn_comparison.py
fixed bug preventing 2 argument execution

@@ -96,7 +96,7 @@ class Main:
             self.instance_meta = gcloud.get_metadata()
             self.run_after_progress()
         else:
-            self.run_classifier_with_id(int(classifier), configuration_id)
+            self.run_classifier_with_id(int(classifier), int(configuration_id))
 
     def run_classifier_with_id(self, classifier_id, configuration_id):
         configuration = configurations[configuration_id]

### 2016-01-15 docs/paper.tex
the final commit before submitting.

@@
 \usepackage{amsmath} %maths
-% Definitions of handy macros can go here
+\usepackage{multirow}
+\usepackage{rotating}
+\usepackage{url}
 
@@
 \newcommand{\fracpartial}[2]{\frac{\partial #1}{\partial  #2}}
-
-% Heading arguments are {volume}{year}{pages}{submitted}{published}{author-full-names}
-
-% \jmlrheading{1}{2000}{1-48}{4/00}{10/00}{Marina Meil\u{a} and Michael I. Jordan}
-
-% Short headings should be running head and authors last names
 
@@
 \title{Location Classification on Tweets}
-\author{\name Erdi \c{C}all{\i} \\ \email erdicalli@gmail.com \\ s4600673}
-
+\author{\name Erdi \c{C}all{\i}  \email e.calli@student.ru.nl}
 \maketitle
-
-\begin{abstract}%
-this is the last thing.
+\begin{abstract}
+Previous research on Twitter user location classification is mostly focusing on multi-class prediction.
+Approaching at the same problem from another perspective, in some cases, it may be enough to answer if someone belongs to a location or not.
+In this perspective, we have compared some models for predicting tweet locations using Binary and Multi-Class Classification.
+We have seen that if the problem at hand is reducible to Binary Classification, it is possible to make much better predictions.
 \end{abstract}
-
-\begin{keywords}
-Supervised Learning, Classification, Twitter, Geolocation
-\end{keywords}
 
@@
 Proliferation of microblogging platforms, such as Twitter, enabled companies to learn valuable information about their products, customers and businesses.
-Twitter, introduced the option to include location information on tweets(geotagging) in 2009\footnote{https://blog.twitter.com/2009/location-location-location}.
+Twitter, introduced the option to include location information on tweets(geotagging) in 2009\footnote{\url{https://blog.twitter.com/2009/location-location-location}}.
 Since then, many applications(i.e Foursquare) and users started embedding this information to enrich the tweet content.
-But this information is not always shared by users.
-Using geotagged tweets to train classification algorithms, it may be possible to infer tweet locations.
+Using geotagged tweets to train classification algorithms, it is proven to be possible to infer tweet locations\cite{cheng2010you}.
 
-Using sentimental analysis\footnote{Twitter as a Corpus for Sentiment Analysis and Opinion Mining.
-A Pak, P Paroubek - LREC, 2010}, a company can learn if its customers are happy with their products or a political figure can get feedback from his/her voters.
+Using sentimental analysis\cite{pak2010twitter}, a company can learn if its customers are happy with their products or a political figure can get feedback from his/her voters.
 The possibilities are endless.
@@
 
-% TODO: REWRITE THIS PART AFTER CHECKING OTHER RESEARCH!
-This problem is first researched in a paper called \textit{You are where you tweet: a content-based approach to geo-locating twitter users}\footnote{http://dl.acm.org/citation.cfm?id=1871535}.
-Then improved with different studies such as \textit{Broadly Improving User Classification via
-Communication-Based Name and Location Clustering on Twitter}\footnote{http://www.aclweb.org/old\_anthology/N/N13/N13-1121.pdf}.
-These studies got accuracy up to 55 percent, not only using the tweet text, but also introducing other factors such as user behaviour.
+Unfortunately geolocation is not shared in most of the tweets and most of the tweets tagged with location are sent from apps or bots.
+Also geotags are containing different granularities such as city, neighbourhood or state.
+Because of those problems most of the data supplied by twitter is filtered out.
 
-% TODO: check your highest recall rate
-Comparing different Machine Learning algorithms implemented in Scikit Learn\footnote{http://scikit-learn.org/}, we have tried to find the best algorithm to approach this problem.
-Introducing different configurations and optimisations, we have achieved a recall rate up to 60\% in binary classification.
+In previous studies, this problem has been solved up to a precision as a multi-class classification problem with different algorithms and assumptions.
+We are introducing binary classification to find the tweets belonging to a specific location.
+
+In this study, different Supervised Learning methods implemented in Scikit Learn\cite{scikit-learn} are tested with different configurations.
+We have also introduced binary classification on location prediction.\footnote{Source code available at \url{http://www.github.com/xarion/waddle}}
 
@@
 
-\section{Data Collection and Analysis}
+Using text mining methods and location tags in tweets, \cite{cheng2010you} redefined this problem.
+\cite{cheng2010you} used only the text data and introduced a method that identifies the words with strong local geo-scope.
+This study achieved up to 51\% accuracy to locate users within a 100 mile radius.
+
+\cite{hecht2011tweets} introduced the $CALGARI$ classifying algorithm specific to this problem, focusing on country and state prediction.
+They got a 72\% accuracy for classifying 4 countries and 30\% accuracy on classifying 18 states.
+
+\cite{eisenstein2010latent} created a geographic topic model to make use of the textual differences in topics based on regions, they got a median distance error of 494 kms.
+
+\cite{wing2011simple} tried to solve this problem using geotagged Wikipedia articles and tweet texts, focusing on predicting the geolocation.
+Their work has obtained a median error of 479 km's for tweets.
+
+\cite{mahmud2012tweet} introduced hierarchical classification methods combined with statistical methods.
+They have achieved 58\%, 66\% and 78\% accuracy on city, state and timezone levels, respectively.
+Also their findings show that users may be able to partially hide their locations, making their tweets untraceable.
+Same researchers revisited the problem in \cite{mahmud2014home}, trying to classify the home location of users, achieving similar results and also introducing movement and location prediction.
+
+\cite{sadilek2012finding} approached this problem introducing the friend information, constructing a friend location graph.
+Their study was able to achieve 77\% to 84.3\% accuracy, relative to available number of friends.
+
+\cite{graham2014world} studied the problems with the baselines accepted by recent studies and explained why location and language classification is not an easy problem and how some of the assumptions are incorrect, such as accepting the device location as user's location.
+
+\section{Method}
+\subsection{Data Collection}
 Using Twitter's sample status streaming api\footnote{https://dev.twitter.com/streaming/reference/get/statuses/sample}, we have collected data.
@@
 
-Investigating the locations the tweets has been sent, we have seen that there are 3306 different locations(location full name in this case) that tweets have been geotagged with.
-
 One problem with the locations is the granularity.
@@
 A selection of 8 top locations, not intersecting each other, is selected from the ones containing the most tweets.
-% TODO: add some figure here, table or histogram of location counts
-
-\section{Experiments}
-% TODO: bag of words reference
 
 \subsection{Empirical Bayes}
-% TODO empirical prior reference
 % TODO twokenize footnote
-In this experiment we have tokenised each tweet using the $twokenize$ module, to convert them to a $bag\ of\ words$, calculate the probability of each "token given location" and probability of each location to find the maximum probability among locations.
+To better understand the data, we have created a posterior with empirical prior\cite{carlin1997bayes} and used MAP estimation\cite{degrooth} to find the best classification result.
+Tokenised each tweet using the $twokenize$ module\cite{gimpel2011part}, to convert them to a $bag\ of\ words$, calculate the probability of each "token given location" and the probability of each location to find their probabilities.
 \begin{equation*}
@@
 \end{equation*}
-With likelihood $p(\mathbf{T} | L)$ and prior $p(\mathbf{L})$. For the prior, instead of assuming a distribution, we have generated an empirical prior and applied MAP estimate to the posterior;
+With likelihood $p(\mathbf{T} | L)$ and prior $p(\mathbf{L})$.
+
+For the prior, instead of assuming a distribution, we have generated an empirical prior and applied MAP estimate to the posterior;
 \begin{equation*}
@@
 This experiment have been tested for 2 different configurations.
-In the first configuration, the collection of sample tweets and geotagged tweet belonging to an individual user are accepted as one document, assuming the same location as geotagged tweet.
+In the first configuration, the collection of sample tweets from a user and the geotagged tweet belonging to same user are accepted as one document, assuming the location of the geotagged tweet.
 In the second configuration, each sample tweet of an individual are accepted as separate documents with same assumption.
 
-The problem with this experiment was, if a token($t_x$) didn't appear in the training dataset, tweets containing this token gots a probability of 0.
-To avoid this problem we have ignored those tokens in the MAP estimate.
+\subsubsection{Implementation}
+First run of the experiment with the whole dataset resulted with 0.02 and 0.04 accuracy rates for the first and second configurations, respectively.
+After this experiment, we have seen that the assumption on the second configuration is better than the first one.
+The rest of this experiment is ran with the second configuration.
 
-%TODO: include results
-\subsection{Scikit Learn}
+One problem with this experiment was, if a token($t_x$) didn't appear in the training dataset, tweets containing this token got a probability of 0.
+To solve this problem, we have ignored those tokens.
+Second run of this classifier resulted with an accuracy rate of 0.05.
+
+\subsubsection{Source Filtering}
+Upon investigating the dataset, we have realised that there are a lot of low quality, automated tweets, coming from 886 different tweet sources(devices or applications that a tweet has been sent from).
+To remove these sources, we have created a whitelist of most used 20 sources that selects applications which real users use to tweet from.
+This reduced the amount of data by around half, to 17040 individual geotagged tweets.
+Third run of the experiment for those 20 sources improved the accuracy to 0.09.
+
+\subsubsection{Location Filtering}
+Investigating the locations the tweets has been sent, we have seen that there are 3306 different locations(location full name in this case) that tweets have been geotagged with.
+Most of them having only 1 tweet.
+We have created another whitelist for locations, only including the top 10.
+This has reduced the dataset to 4751 individual geotagged tweets.
+Taking a closer look to those 10 locations, we have seen that there are 1 neighbourhood, 2 states and 7 cities.
+To have finer class definitions, we have removed those 2 states from location whitelist.
+Running the experiment for the last time, we have acquired an accuracy of 0.11.
+Which doesn't seem better than making random classifications for 8 locations.
+
+\subsection{Scikit Learn - Multinomial Naive Bayes}
+This experiment uses the Multinomial Naive Bayes model to predict classes.
+This model captures information on documents as an ordered sequence of tokens\cite{mccallum1998comparison}, using a Multinomial Distribution.
+We have used the method implemented in Scikit Learn\cite{scikit-learn}(sklearn, v0.17).
+
+Also, in this experiment, we have redefined the data configurations.
+For the first data configuration, all tweets of a user are tagged with the original tweet's geotag location.
+For the second configuration, we have ignored the user history and only used the geotagged tweets.
+
+These implementations also had a different structure.
+Instead of token counts used in the first experiment, we have used tf-idf scores.
+Also sparse matrix implementation of Numpy is used to represent those frequencies by default.
+We have stopped using the $twokenize$ module and switched to the internal tokenizer of sklearn.
+
+\subsubsection{Multinomial Naive Bayes}
+
+For this experiment, MultinomialNB(Multinomial Naive Bayes) implementation is selected.
+This implementation has achieved a higher macro accuracy results of 0.19, 0.24 for first and second configurations, respectively.
+But when we investigated the micro accuracy we have seen that the classifier almost always predicted the location with highest amount of tweets.
+
+\subsubsection{Normalisation of Documents per Class}
+To prevent the problem in the last experiment, we have normalised the dataset by accepting equal amount of documents per class.
+Upon normalising the number of documents per class, we have achieved accuracy rates of 0.29, 0.42 for first and second data configurations.
+
+\subsubsection{Ngrams}
+To improve the results found in the last experiment, we have tried Ngrams in range (1,2).
+It did not result with an improvement in accuracy.
+The accuracy has decreased by 0.003 for both configurations.
+
+\subsubsection{Binary Classification}
+To be able to answer the question, which tweets are from given a location, we have changed our multi-class classification problem to a binary classification problem.
+Running tests to classify tweets from $Manhattan,\ NY$ by including previous improvements and ngrams in range (1,2) we have achieved accuracy rates of 0.71, 0.62 for first and second data configurations, respectively.
+
+\subsection{Scikit Learn - Algorithm Comparison}
 This experiment compares the classification methods implemented in Scikit Learn(sklearn)(v0.17) library with different configurations.
+Sklearn implements various classification methods such as, Logistic Regression, Perceptron, Support Vector Classifiers and etc.
+We have compared the sklearn methods under supervised learning\footnote{http://scikit-learn.org/stable/supervised\_learning.html}, applicable to classification and able to work with sparse matrices.
+We have also tried various parameters for those algorithms.
+Resulting set of algorithms and parameters was containing 22 combinations.
 
-% Acknowledgements should go at the end, before appendices and references
+\begin{enumerate}
+\scriptsize
 
-% \acks{We would like to acknowledge support for this project
-% from the National Science Foundation (NSF grant IIS-9988642)
-% and the Multidisciplinary Research Program of the Department
-% of Defense (MURI N00014-00-1-0637). }
+\item LogisticRegressionCV: a linear model for classification.
+Uses a logistic function to calculate the class probabilities are of a single trial.
+This version uses cross validation to find optimal values for parameters.
+\item SGDClassifier: Stochastic Gradient Descent learning model supporting multiple loss functions and penalties. 
+\begin{enumerate}
+\item SGDClassifier(loss="hinge"): Hinge is a commonly used convex loss function for classification.
+\item SGDClassifier(loss="log"): Converts SGD to a probabilistic logistic regression classifier.
+\item SGDClassifier(loss="modified\_huber"): Hinge with a setting, $\gamma=2$
+\item SGDClassifier(loss="squared\_hinge"): Quadratically penalised hinge.
+\item SGDClassifier(loss="perceptron"): Linear loss function used with the Perceptron algorithm.
+\item SGDClassifier(loss="squared\_loss"): Least squares loss function.
+\item SGDClassifier(loss="huber"): Similar to squared\_loss but switches from squared to linear after a threshold.
+\item SGDClassifier(loss="epsilon\_insensitive"): Linear loss function, ignoring errors less than the threshold, epsilon.
+\item SGDClassifier(loss="squared\_epsilon\_insensitive"): Squared version of epsilon\_insensitive.
+\end{enumerate}
+\item Perceptron: Same as SGDClassifier(loss="perceptron") with a constant learning rate and different default parameters.
+\item PassiveAggressiveClassifier: Similar to Perceptron. Instead of using a learning rate, uses a regularisation term.
+\begin{enumerate}
+\item PassiveAggressiveClassifier(loss="hinge")
+\item PassiveAggressiveClassifier(loss="squared\_hinge")
+\end{enumerate}
+\item SVC: Classifier model using Support Vector Machines. Creates a high or infinite dimensional one or many hyperplanes and clusters classes on that space.
+\begin{enumerate}
+\item SVC(kernel='poly'): Polynomial kernel for SVM.
+\item SVC(kernel='sigmoid'): Sigmoid kernel for SVM.
+\end{enumerate}
+\item LinearSVC: SVM with linear kernel.
+\item KNeighborsClassifier: K-Nearest Neighbours classifier.
+\begin{enumerate}
+\item KNeighborsClassifier(n\_neighbors=8, weights="uniform"): Uses uniform weights to classify neighbours.
+\item KNeighborsClassifier(n\_neighbors=8, weights="distance"): Inverse of distance weights. Closer neighbours have a greater influence on classification.
+\end{enumerate}
+\item MultinomialNB: Multinomial Naive Bayes, assumes a Multinomial Distribution of features.
+\item BernoulliNB: Bernoulli Naive Bayes, assumes a Bernoulli Distribution of features.
+\item DecisionTreeClassifier: Creates a rule based decision tree inferred from data for predict.
+\item AdaBoostClassifier(n\_estimators=170): Fits N($n\_estimators$) Decision Tree Classifiers to samples from training data.
+Then assigns them weights based on errors.
+Using those weights, casts a voting to find the best prediction.
+\end{enumerate}
+\normalsize
+We have tried those 22 combination of algorithms and parameters, with 3 different data configuration parameters; 
+\footnotesize
+\begin{enumerate}
+\item Binary Classification
+\item Include user history
+\item Ngram
+\end{enumerate}
+\normalsize
 
-% Manual newpage inserted to improve layout of sample file - not
-% needed in general before appendices/bibliography.
+Resulting with 8 different data configurations and 176 different combinations.
 
+\subsubsection{Precision, Recall, Fscore}
+To represent the results of those 176 combination, micro precision, recall and fscore are used.
+\subsubsection{Execution}
+To execute those tasks, we have decided to use Google Cloud instances.
+Google Cloud offers 300\$ trial usage for users who want to try out their services and it allows up to 32 cores in this trial period.
+We have implemented an argument to execute all those tasks on multiple google cloud instances, in parallel.
+Created a template operating system including an executable version of our implementation.
+Created 15 two core execution instances from this template, 1 MongoDB instance to serve data, store results and progress.
+It took 35 mins to finish the execution of those 176 tasks.
+
+\section{Results}
+Using Scikit-learn\cite{scikit-learn} we tried location classification using 22 models on 8 different settings.
+Those results have been shared in Figure 1 and 2.
+Figures contain 12 subfigures, showing precision, recall and f1scores for different combinations of ngram(1,2) and include user history(0,1) parameters.
+Each figure contains the relative micro results for 22 different models using the Box plots\cite{mcgill1978variations}.
+Each box plot shows outliers with plusses(+), max and min value as dashes, a bounding box of upper and lower quartiles, a red dash showing the mean(instead of median).
+Because each class contains equal amount of data, mean of micro precision, recall and f1score can be interpreted as the macro precision, recall and f1score.
+Each subfigure contains a green line indicating the baseline macro precision, recall or f1score.
+In subfigures, models have been labelled with numbers ranging between 0 and 21.
+Those labels are given in Table 1.
+
+Tall boxes in the figures represent unstable results, mostly caused by models predicting one or more classes better than others or failing to classify one or more classes not as good as others.
+
+\begin{table}
+\scriptsize
+    \begin{tabular}{|c|l||c|l|}
+	\hline 
+		0 & LogisticRegressionCV & 1 & SGDClassifier(loss="hinge") \\ \hline
+		2 & SGDClassifier(loss="log")&  3 & SGDClassifier(loss="modified\_huber") \\ \hline
+		4 & SGDClassifier(loss="squared\_hinge") & 5 & SGDClassifier(loss="perceptron") \\ \hline
+		6 & SGDClassifier(loss="squared\_loss") & 7 & SGDClassifier(loss="huber")\\ \hline
+		8 &SGDClassifier(loss="epsilon\_insensitive") & 9 & SGDClassifier(loss="squared\_epsilon\_insensitive") \\ \hline
+		10 & Perceptron & 11 & PassiveAggressiveClassifier(loss="hinge")\\ \hline
+		12 & PassiveAggressiveClassifier(loss="squared\_hinge") & 13 & SVC(kernel="poly") \\ \hline
+		14 & SVC(kernel="sigmoid") & 15 & LinearSVC\\ \hline
+		16 & KNeighborsClassifier(weights="uniform") & 17 & KNeighborsClassifier(weights="distance") \\ \hline
+		18 & MultinomialNB & 19 & BernoulliNB\\ \hline
+		20 & DecisionTreeClassifier & 21 & AdaBoostClassifier\\ \hline
+	\end{tabular}
+	\caption{Classifier Model Labels}
+\end{table}
+\normalsize
+\subsection{Parameters}
+
+\subsubsection{Ngram}
+Effects of including token bigrams with unigrams did not have major implications in the results. This parameter has changed the average f1scores of models by +0.04 to -0.05.
+
+\subsubsection{Including User History}
+Including history in the training and testing phases reduced the classifier performances in almost all cases. Overall average decrease in f1scores was 0.076 with values 
+ranging from 0.21 to -0.09.
+
+\subsection{Multi-Class Classification}
+Baseline for Multi-Class classification is 0.125.
+Since we have 8 classes in total for this task, if a model has predicted only one class, that baseline value would be the macro precision, recall and f1score.
+For this task, top result was achieved by LogisticRegressionCV with an fscore of 0.443 and a recall of 0.50.
+
+\subsection{Binary Classification}
+Baseline for this task is 0.5. With bigrams, BernoulliNB, SGD with modified huber loss function and SGD with hinge loss function have achieved the top 3 f1scores of 0.734, 0.726, 0.72, respectively. 
+Only with unigrams BernoulliNB, MultinomialNB and PassiveAgressiveClassifier with hinge loss function achieved the top 3 f1scores of 0.726, 0.719 and 0.717, respectively.
+
+\section{Conclusion and Discussion}
+In this research we have seen that binary classification on tweet locations can get up to 73\% macro precision.
+Compared to previous studies dealing with this problem in a multi-class perspective, if the task is to predict if a tweet is belonging to one particular location, this looks like a promising result.
+But the fact of all our data belonging to geotagged tweets may compromising the validity of these results.
+
+Refining the training dataset with less application generated content and more data would yield with more authentic research result.
+\noindent\begin{sidewaysfigure}
+    \centering
+    \includegraphics[width=\paperwidth]{figures/binary.eps}
+    \caption{Binary classification results}
+\end{sidewaysfigure}
+\noindent\begin{sidewaysfigure}
+    \centering
+    \includegraphics[width=\paperwidth]{figures/multi_class}
+    \caption{Multi-Class classification results}
+\end{sidewaysfigure}
 \newpage
 
-\appendix
-\section*{Appendix A.}
-\label{app:theorem}
-
-% Note: in this sample, the section number is hard-coded in. Following
-% proper LaTeX conventions, it should properly be coded as a reference:
-
-%In this appendix we prove the following theorem from
-%Section~\ref{sec:textree-generalization}:
-
-In this appendix we prove the following theorem from
-Section~6.2:
-
-\noindent
-{\bf Theorem} {\it Let $u,v,w$ be discrete variables such that $v, w$ do
-not co-occur with $u$ (i.e., $u\neq0\;\Rightarrow \;v=w=0$ in a given
-dataset $\dataset$). Let $N_{v0},N_{w0}$ be the number of data points for
-which $v=0, w=0$ respectively, and let $I_{uv},I_{uw}$ be the
-respective empirical mutual information values based on the sample
-$\dataset$. Then
-\[
-	N_{v0} \;>\; N_{w0}\;\;\Rightarrow\;\;I_{uv} \;\leq\;I_{uw}
-\]
-with equality only if $u$ is identically 0.} \hfill\BlackBox
-
-\noindent
-{\bf Proof}. We use the notation:
-\[
-P_v(i) \;=\;\frac{N_v^i}{N},\;\;\;i \neq 0;\;\;\;
-P_{v0}\;\equiv\;P_v(0)\; = \;1 - \sum_{i\neq 0}P_v(i).
-\]
-These values represent the (empirical) probabilities of $v$
-taking value $i\neq 0$ and 0 respectively.  Entropies will be denoted
-by $H$. We aim to show that $\fracpartial{I_{uv}}{P_{v0}} < 0$....\\
-
-{\noindent \em Remainder omitted in this sample. See http://www.jmlr.org/papers/ for full paper.}
-
-\vskip 0.2in
-\bibliography{sample}
-
+\bibliographystyle{alpha}
+\bibliography{paper}
 \end{document}

### 2016-01-15 plots.py

@@ -1,0 +1,78 @@
+import matplotlib
+from matplotlib import pyplot as plt
+
+from data.MongoDB import db
+
+binary_classification = False
+
+matplotlib.rcParams.update({'font.size': 3})
+
+baseline = None
+if binary_classification:
+    baseline = 1. / 2
+else:
+    baseline = 1. / 8
+
+mean_line_props = dict(linestyle='--', color='r')
+median_line_props = dict(linestyle='None')
+
+
+def plot(ngram, history, sub_index, axes, title):
+    binary_classification_result_docs = db.results_collection.find(
+            {"binary_classification": binary_classification, "ngram": ngram, "include_user_history": history}).sort(
+            "classifier_id", 1)
+
+    precision_results = []
+    recall_results = []
+    f1score_results = []
+
+    labels = list()
+    empty_results = None
+    for result in binary_classification_result_docs:
+        if "result" in result:
+            precision_results.append(map(float, result["result"]["precision"]))
+            recall_results.append(map(float, result["result"]["recall"]))
+            f1score_results.append(map(float, result["result"]["f1score"]))
+            if empty_results is None:
+                empty_results = [.0] * len(result["result"]["precision"])
+        else:
+            precision_results.append(empty_results)
+            recall_results.append(empty_results)
+            f1score_results.append(empty_results)
+
+        labels.append(result["classifier_id"])
+
+    axes[0][sub_index].set_title(title)
+
+    axes[0][sub_index].boxplot(precision_results, labels=labels, showmeans=True, meanline=True,
+                               meanprops=mean_line_props, medianprops=median_line_props)
+    axes[0][sub_index].plot([0, 23], [baseline, baseline], "g-")
+    axes[0][sub_index].set_ylabel('Precision')
+    axes[0][sub_index].set_ylim([0, 1])
+
+    axes[1][sub_index].boxplot(recall_results, labels=labels, showmeans=True, meanline=True, meanprops=mean_line_props,
+                               medianprops=median_line_props)
+    axes[1][sub_index].plot([0, 23], [baseline, baseline], "g-")
+    axes[1][sub_index].set_ylabel('Recall')
+    axes[1][sub_index].set_ylim([0, 1])
+
[…]

### 2016-01-15 result_comparison.py

@@ -1,0 +1,51 @@
+import numpy as np
+
+from data.MongoDB import db
+
+# history = db.results_collection.find(
+#             {"binary_classification": False, "ngram": 2, "include_user_history": False}).sort(
+#             "classifier_id", 1)
+#
+# history_means = []
+# for result in history:
+#     if "result" in result:
+#         history_means.append(np.mean(map(float, result["result"]["f1score"])))
+#     else:
+#         history_means.append(.5)
+#
+# nohistory = db.results_collection.find(
+#             {"binary_classification": False, "ngram": 2, "include_user_history": False}).sort(
+#             "classifier_id", 1)
+#
+# nohistory_means = []
+# for result in nohistory:
+#     if "result" in result:
+#         nohistory_means.append(np.mean(map(float, result["result"]["f1score"])))
+#     else:
+#         nohistory_means.append(.5)
+#
+# for i in range(0, len(classifier_names)):
+#     if nohistory_means[i] < history_means[i]:
+#         print classifier_names[i]
+#         print nohistory_means[i] - history_means[i]
+#
+# print np.mean(history_means) - np.mean(nohistory_means)
+from sklearn_comparison import configurations
+
+results = db.results_collection.find({"binary_classification": True, "include_user_history": True})
+
+resultz = []
+
+for result in results:
+    if "result" in result:
+        resultz.append({"f1": np.mean(map(float, result["result"]["f1score"])), "precision": np.mean(map(float, result["result"]["precision"])), "recall": np.mean(map(float, result["result"]["recall"])), "classifier": result["classifier"], "configuration": configurations[result["configuration_id"]]})
+
+
+
+def get_value(d):
+    return d["f1"]
+
+
+fin = sorted(resultz, key=get_value)
+
+print fin

### 2016-01-19 docs/paper.tex
fixed misuse of micro precision/recall/fscore

@@
 This implementation has achieved a higher macro accuracy results of 0.19, 0.24 for first and second configurations, respectively.
-But when we investigated the micro accuracy we have seen that the classifier almost always predicted the location with highest amount of tweets.
+But when we investigated the accuracy we have seen that the classifier almost always predicted the location with highest amount of tweets.
 
@@
 \subsubsection{Precision, Recall, Fscore}
-To represent the results of those 176 combination, micro precision, recall and fscore are used.
+To represent the results of those 176 combination, precision, recall and fscore are used.
 \subsubsection{Execution}
@@
 Figures contain 12 subfigures, showing precision, recall and f1scores for different combinations of ngram(1,2) and include user history(0,1) parameters.
-Each figure contains the relative micro results for 22 different models using the Box plots\cite{mcgill1978variations}.
+Each figure contains the relative results for 22 different models using the Box plots\cite{mcgill1978variations}.
 Each box plot shows outliers with plusses(+), max and min value as dashes, a bounding box of upper and lower quartiles, a red dash showing the mean(instead of median).
-Because each class contains equal amount of data, mean of micro precision, recall and f1score can be interpreted as the macro precision, recall and f1score.
+Because each class contains equal amount of data, mean of precision, recall and f1score can be interpreted as the macro precision, recall and f1score.
 Each subfigure contains a green line indicating the baseline macro precision, recall or f1score.

### 2016-03-08 docs/paper.tex
Finalized the introduction

@@
 \begin{abstract}
-Previous research on Twitter user location classification is mostly focusing on multi-class prediction.
+% Previous research on Twitter user location classification is mostly focusing on multi-class prediction.
 Approaching at the same problem from another perspective, in some cases, it may be enough to answer if someone belongs to a location or not.
@@
 We have seen that if the problem at hand is reducible to Binary Classification, it is possible to make much better predictions.
+
 \end{abstract}
@@
 
-Proliferation of microblogging platforms, such as Twitter, enabled companies to learn valuable information about their products, customers and businesses.
-Twitter, introduced the option to include location information on tweets(geotagging) in 2009\footnote{\url{https://blog.twitter.com/2009/location-location-location}}.
-Since then, many applications(i.e Foursquare) and users started embedding this information to enrich the tweet content.
-Using geotagged tweets to train classification algorithms, it is proven to be possible to infer tweet locations\cite{cheng2010you}.
+Twitter is an online platform that lets users to share posts with their followers, limited with at most 140 characters, called as tweets.
+Tweets can be almost anything that we share on internet; a personal message stating our views, a link to an article, a picture and etc..
+There are no boundaries except the character limit.
+In 2009, Twitter introduced an option to include geographic location(geolocation) information on tweets\footnote{\url{https://blog.twitter.com/2009/location-location-location}}.
+Since then, a lot of twitter users have been sharing their geolocation with their tweets(or geotagging their tweets).
+Depending on the context of the tweet, having the geolocation may be very valuable.
+For example a tweet about a Pizza franchise or a political campaign, if geotagged, may point to an improvement with exact location or contribute to the statistics of a specific area.
+Unfortunately, geolocation of a tweet is not shared by default or in other words, most of the tweets are not geotagged, unless explicitly specified.
+Inferring the geolocation of a tweet is what this paper is about.
 
-Using sentimental analysis\cite{pak2010twitter}, a company can learn if its customers are happy with their products or a political figure can get feedback from his/her voters.
-The possibilities are endless.
-Incorporating this information with geolocation may be valuable in lots of situations for politicians, businesses and other parties.
+To be able to infer this information, we can try to use linguistic habits shared by the people who are in the same city.
+As humans, our spatial cognition deals with updating and managing the knowledge about our environment.
+Spatial cognition changes when we move between environments, but as we stay within the boundaries of a high level environment(i.e.
+a city), there may be some high level constants that doesn't change.
+If some of these constants are shared commonly between people, it may lead them to have similar linguistic habits, in this case, textual features in their tweets.
+If we group the geotagged tweets sent from a city, it may be possible to extract these features, if they exist.
 
-Unfortunately geolocation is not shared in most of the tweets and most of the tweets tagged with location are sent from apps or bots.
-Also geotags are containing different granularities such as city, neighbourhood or state.
-Because of those problems most of the data supplied by twitter is filtered out.
+Using similar features, previous research tries to determine the geolocation of a tweet using multi-class classification algorithms.
+These methods are trying to determine the most likely geolocation for a tweet from a list(e.g.
+cities in a country).
+It is sometimes hard to do that, because we need data from all cities.
+Also the algorithms and the implementations become more complicated.
+Thus, in cases where we just want to know if someone is from a city or not, this approach becomes unnecessarily heavy.
+In this research, we are simplifying this problem by using binary classification algorithms, which are trying to determine if a tweet belongs to a location(i.e.
+New York City) or not.
 
-In previous studies, this problem has been solved up to a precision as a multi-class classification problem with different algorithms and assumptions.
-We are introducing binary classification to find the tweets belonging to a specific location.
-
-In this study, different Supervised Learning methods implemented in Scikit Learn\cite{scikit-learn} are tested with different configurations.
-We have also introduced binary classification on location prediction.\footnote{Source code available at \url{http://www.github.com/xarion/waddle}}
+Revolving around our hypothesis, the research question we're trying to answer is: "Are there textual features in tweets, that are common for people in the same city?
+If there are, can they help us determine if a tweet is from that city, or not?"
 

### 2016-03-09 docs/paper.tex
rewritten data collection and filters

@@
 
-To be able to infer this information, we can try to use linguistic habits shared by the people who are in the same city.
+To be able to infer this information, we can try to use linguistic habits shared by the people who are within the same location.
 As humans, our spatial cognition deals with updating and managing the knowledge about our environment.
 Spatial cognition changes when we move between environments, but as we stay within the boundaries of a high level environment(i.e.
-a city), there may be some high level constants that doesn't change.
+state, city, borough), there may be some high-level constants that doesn't change.
 If some of these constants are shared commonly between people, it may lead them to have similar linguistic habits, in this case, textual features in their tweets.
-If we group the geotagged tweets sent from a city, it may be possible to extract these features, if they exist.
+If we group the geotagged tweets sent within a high-level location, it may be possible to extract these features, if they exist.
 
@@
 Also the algorithms and the implementations become more complicated.
-Thus, in cases where we just want to know if someone is from a city or not, this approach becomes unnecessarily heavy.
-In this research, we are simplifying this problem by using binary classification algorithms, which are trying to determine if a tweet belongs to a location(i.e.
-New York City) or not.
+Thus, in cases where we just want to know if someone is within a state/city/borough or not, this approach becomes unnecessarily heavy.
+In this research, we are simplifying this problem by using binary classification algorithms, which are trying to determine if a tweet sent within the boundaries of a location(i.e.
+Manhattan, NY) or not.
 
-Revolving around our hypothesis, the research question we're trying to answer is: "Are there textual features in tweets, that are common for people in the same city?
-If there are, can they help us determine if a tweet is from that city, or not?"
+Revolving around our hypothesis, the research question we're trying to answer is: "Are there textual features in tweets, that are common for people within the same location?
+If there are, can they help us determine if a tweet is sent within that high-level location, or not?"
 
@@
 
-Using text mining methods and location tags in tweets, \cite{cheng2010you} redefined this problem.
+% Using text mining methods and location tags in tweets, \cite{cheng2010you} redefined this problem.
 \cite{cheng2010you} used only the text data and introduced a method that identifies the words with strong local geo-scope.
@@
 
-\cite{hecht2011tweets} introduced the $CALGARI$ classifying algorithm specific to this problem, focusing on country and state prediction.
+% \cite{hecht2011tweets} introduced the $CALGARI$ classifying algorithm specific to this problem, focusing on country and state prediction.
 They got a 72\% accuracy for classifying 4 countries and 30\% accuracy on classifying 18 states.
 
-\cite{eisenstein2010latent} created a geographic topic model to make use of the textual differences in topics based on regions, they got a median distance error of 494 kms.
+% \cite{eisenstein2010latent} created a geographic topic model to make use of the textual differences in topics based on regions, they got a median distance error of 494 kms.
 
-\cite{wing2011simple} tried to solve this problem using geotagged Wikipedia articles and tweet texts, focusing on predicting the geolocation.
+% \cite{wing2011simple} tried to solve this problem using geotagged Wikipedia articles and tweet texts, focusing on predicting the geolocation.
 Their work has obtained a median error of 479 km's for tweets.
 
-\cite{mahmud2012tweet} introduced hierarchical classification methods combined with statistical methods.
+% \cite{mahmud2012tweet} introduced hierarchical classification methods combined with statistical methods.
 They have achieved 58\%, 66\% and 78\% accuracy on city, state and timezone levels, respectively.
@@
 
-\cite{sadilek2012finding} approached this problem introducing the friend information, constructing a friend location graph.
+% \cite{sadilek2012finding} approached this problem introducing the friend information, constructing a friend location graph.
 Their study was able to achieve 77\% to 84.3\% accuracy, relative to available number of friends.
 
-\cite{graham2014world} studied the problems with the baselines accepted by recent studies and explained why location and language classification is not an easy problem and how some of the assumptions are incorrect, such as accepting the device location as user's location.
+% \cite{graham2014world} studied the problems with the baselines accepted by recent studies and explained why location and language classification is not an easy problem and how some of the assumptions are incorrect, such as accepting the device location as user's location.
 
 \section{Method}
-\subsection{Data Collection}
-Using Twitter's sample status streaming api\footnote{https://dev.twitter.com/streaming/reference/get/statuses/sample}, we have collected data.
-This api returns approximately 1\% of the public tweets from all around the world.
-We have filtered this data to reduce the problem space to only location classification.
-Our filter selects only the geotagged English tweets, sent within the United States.
-Running this collector for 1 month, we have collected a dataset consisting of 33112 individual tweets, each from a unique user.
-We have also collected a sample of 40 tweets from those users, if their timelines are public, to enrich the dataset.
+\subsection{Data Collection and Filtering}
 
-Upon investigating this dataset, we have realised that there are a lot of low quality, automated tweets, coming from 886 different tweet sources(devices or applications that a tweet has been sent from).
-To remove these sources, we have created a whitelist of most used 20 sources that selects applications which real users use to tweet from.
-This reduced the amount of data by around 50\%, to 17040 individual geotagged tweets.
+Using Twitter's sample status streaming api\footnote{https://dev.twitter.com/streaming/reference/get/statuses/sample}, we have sampled the public tweets.
+This api samples approximately 1\% of all the public tweets around the world.
+To be able to find the tweets that are relevant to our task, we have applied some filters to this api.
 
-One problem with the locations is the granularity.
-A location can appear as a state(New York, US), a city(New York, NY) or a neighbourhood(Manhattan, NY).
-A selection of 8 top locations, not intersecting each other, is selected from the ones containing the most tweets.
+First of all, we have applied a filter to ignore non-geotagged tweets.
+The high-level location information contained within each geotag will be used as the label of a tweet.
+These labels will be used to train our algorithms, and they will be compared with the predicted results to see how accurate our methods are.
+
+Also, we are not interested with tweets in different languages.
+Having tweets from different languages would introduce a complicated variable and make our results hard to interpret.
+Therefore, we choose English as our language of interest, because we assumed that English is the most common language that people tweet, thus it would yield the biggest dataset(compared to other languages).
+Samples from twitter contain the language information, we have used this information to filter tweets which are not English.
+
+Considering the language assumption, having tweets from non-English speaking countries would be unnecessary.
+Also, having tweets from different countries would introduce another variable.
+Assuming that United States would yield the biggest dataset(compared to other countries), we have limited the tweets we collected to United States.
+
+Running the data collector for 1 month, we have collected a dataset consisting of 33112 tweets, geotagged within United States, tagged as English and each from a unique user.
+
+Since each tweet is consisting of at most 140 characters, our dataset might not be enough to extract the textual features we're interested in.
+To enrich our database, we assumed that our users are not actively travelling.
+Therefore, we have collected past 40(at most) tweets of these users and attached them to the sampled tweet as history.
+
+Assuming we had a dataset, big enough for the task, we examined a small sample of it.
+In this sample, we have seen many examples which were not composed by humans, but bots(e.g.
+"\textit{Police department activity on \#I95 SB at 3rd Avenue; Exit 3}").
+Twitter also gives the information on which application is used to send a tweet.
+We have examined this information, called \textit{source}, to filter these tweets.
+Grouping and sorting them by the number of tweets, we were able to see which sources are most relevant for our study.
+Annotating the most relevant 20(e.g.
+\textit{Twitter for iPhone}, \textit{Facebook} and etc.) we have created the whitelist filter for tweet sources.
+
+In our examination, we have also seen a variety of geotag names which represent the high-level locations we're interested in(e.g.
+\textit{Mississippi, USA}, \textit{Manhattan, NY} and etc.).
+When we checked the number of tweets per location, we have seen that there are 4898 unique locations in the whole dataset with different granularities(e.g.
+state, city, borough and etc).
+We have picked 8 of the most common locations(e.g.
+\textit{Manhattan, NY}, \textit{Los Angeles, CA}, \textit{Houston, TX} and etc.).
+
+When we applied all these filters, we ended up having a dataset containing 8 locations, each of them having between 986 to 180 tweets.
 

### 2016-03-09 docs/paper.tex
latest version

@@
 
-\section{Method}
+\section{Methods}
+
 \subsection{Data Collection and Filtering}
@@
 
-Since each tweet is consisting of at most 140 characters, our dataset might not be enough to extract the textual features we're interested in.
-To enrich our database, we assumed that our users are not actively travelling.
-Therefore, we have collected past 40(at most) tweets of these users and attached them to the sampled tweet as history.
-
 Assuming we had a dataset, big enough for the task, we examined a small sample of it.
@@
 \textit{Mississippi, USA}, \textit{Manhattan, NY} and etc.).
-When we checked the number of tweets per location, we have seen that there are 4898 unique locations in the whole dataset with different granularities(e.g.
+When we checked the number of tweets per location, we have seen that there are 3306 unique locations in the whole dataset with different granularities(e.g.
 state, city, borough and etc).
-We have picked 8 of the most common locations(e.g.
-\textit{Manhattan, NY}, \textit{Los Angeles, CA}, \textit{Houston, TX} and etc.).
+Upon examining these locations, we have seen that it was not worth merging these locations with small granularities(e.g.
+boroughs) to higher levels(e.g.
+cities).
+Also we are not interested in location definitions higher than cities.
+Therefore, we have picked 8 of the most common locations(e.g.
+\textit{Manhattan, NY}, \textit{Los Angeles, CA}, \textit{Houston, TX} and etc.) ignoring states.
 
-When we applied all these filters, we ended up having a dataset containing 8 locations, each of them having between 986 to 180 tweets.
+When we applied all these filters, we ended up having a dataset containing 8 locations, each of them having between 986 to 180 tweets, summing up to 3176.
+
+Since each tweet is limited by 140 characters, and our dataset is shrank to only 4751 tweets, our dataset might not be enough to extract the textual features we are interested in.
+To enrich our database, we assumed that our users are always sending tweets from the same location.
+Therefore, we have collected past 40 tweets of these users and attached them to the sampled tweet as \textit{past tweets}.
+
+In all our experiments, we have splitted our datasets 50\% by 50\% training and test datasets.
+\subsection{Tools}
+sklearn python mongo
 
 \subsection{Empirical Bayes}
-% TODO twokenize footnote
-To better understand the data, we have created a posterior with empirical prior\cite{carlin1997bayes} and used MAP estimation\cite{degrooth} to find the best classification result.
-Tokenised each tweet using the $twokenize$ module\cite{gimpel2011part}, to convert them to a $bag\ of\ words$, calculate the probability of each "token given location" and the probability of each location to find their probabilities.
+
+In the process of filtering data, we have implemented an Empirical Bayes\cite{carlin1997bayes} classifier using MAP estimation\cite{degrooth} to perform multi-class classification.
+We chose Empirical Bayes because it was easy to implement and it was not assuming any independency between data points, which was required when using past tweets, which may be dependent to each other.
+Implementing this algorithm also helped us to understand the nature of data, and also we somehow tried to reproduce results similar to previous research.
 \begin{equation*}
 \begin{split}
-\mathbf{T} &= Tokens \\
+\mathbf{T}_i & = \text{tokens of $i$th tweet }\\
+t_{ni} & = \text{$n$th token of $i$th tweet }\\
 L &= Location \\
-p(L|\mathbf{T}) &= \frac{p(\mathbf{T} | L)p(L)}{p(T)}
+p(L|\mathbf{T}_i) &= \frac{p(\mathbf{T}_i | L)p(L)}{p(\mathbf{T}_{i})} 
 \end{split}
 \end{equation*}
-With likelihood $p(\mathbf{T} | L)$ and prior $p(\mathbf{L})$.
+To train this algorithm, we have created a likelihood($p(t | L)$) and an empirical prior.
+To calculate the likelihood, we have tokenized each tweet using the $twokenize$ module\cite{gimpel2011part}, labelled them with the location and calculated the "probability of a token given location".
+As for the prior we have generated the empirical prior, which is the occurrences of a location divided by the number of data points.
+As a result of training, we have stored the likelihood and prior.
 
-For the prior, instead of assuming a distribution, we have generated an empirical prior and applied MAP estimate to the posterior;
+To predict where a tweet has been sent from we have applied MAP estimate to the Empirical Bayes.
+For each tweet in our test dataset, we have tokenized the tweet, queried the likelihood values for each token and location, combined these probabilities per location, applied the empirical prior and choose the location with the maximum probability.
 \begin{equation*}
-\hat{L} = \arg\max_L\{p(\mathbf{T} | L) P(L)\}
+\hat{L} = \arg\max_L\{p(\mathbf{T}_i | L) p(L)\}\\
 \end{equation*}
-where;
 \begin{equation*}
-\begin{split}
-p(\mathbf{T} | L) &= \prod_i{p(t_i|L)}\\
-\end{split}
+p(\mathbf{T_i} | L) = \prod_n{p(t_{ni}|L)}
 \end{equation*}
-Empirical prior $p(L)$ is referring to the probability of a location L in the training data.
 
-This experiment have been tested for 2 different configurations.
-In the first configuration, the collection of sample tweets from a user and the geotagged tweet belonging to same user are accepted as one document, assuming the location of the geotagged tweet.
-In the second configuration, each sample tweet of an individual are accepted as separate documents with same assumption.
+To test the assumption we made to enrich our dataset, this experiment was ran with 2 configurations one using past tweets and other using sampled tweets.
+In the first configuration, we labelled each past tweet with the high-level location of the related sample(tweet).
+We have used this configuration to test our assumption of users are always sending tweets within same high-level location, thus we can use their pasts.
+In the second configuration, we only used the sample tweets and their high-level locations as labels.
 
-\subsubsection{Implementation}
-First run of the experiment with the whole dataset resulted with 0.02 and 0.04 accuracy rates for the first and second configurations, respectively.
-After this experiment, we have seen that the assumption on the second configuration is better than the first one.
-The rest of this experiment is ran with the second configuration.
+First run of the experiment, without applying filters to the dataset, resulted with 0.02 and 0.04 accuracy rates for the first and second configurations, respectively.
+After this experiment, we have seen that the assumption on the first configuration did not improve our results, so this is not likely to be true.
+The rest of this Empirical Bayes experiment was ran only with the sampled tweets.
 
-One problem with this experiment was, if a token($t_x$) didn't appear in the training dataset, tweets containing this token got a probability of 0.
-To solve this problem, we have ignored those tokens.
-Second run of this classifier resulted with an accuracy rate of 0.05.
-
-\subsubsection{Source Filtering}
-Upon investigating the dataset, we have realised that there are a lot of low quality, automated tweets, coming from 886 different tweet sources(devices or applications that a tweet has been sent from).
-To remove these sources, we have created a whitelist of most used 20 sources that selects applications which real users use to tweet from.
-This reduced the amount of data by around half, to 17040 individual geotagged tweets.
-Third run of the experiment for those 20 sources improved the accuracy to 0.09.
-
-\subsubsection{Location Filtering}
-Investigating the locations the tweets has been sent, we have seen that there are 3306 different locations(location full name in this case) that tweets have been geotagged with.
-Most of them having only 1 tweet.
-We have created another whitelist for locations, only including the top 10.
-This has reduced the dataset to 4751 individual geotagged tweets.
-Taking a closer look to those 10 locations, we have seen that there are 1 neighbourhood, 2 states and 7 cities.
-To have finer class definitions, we have removed those 2 states from location whitelist.
-Running the experiment for the last time, we have acquired an accuracy of 0.11.
-Which doesn't seem better than making random classifications for 8 locations.
+One problem with this experiment was, if a token($t_x$) didn't appear in the training dataset, we didn't know the likelihood of that token.
+So if tweet contains a token which did not appear on that location in training, that tweet got a probability of 0 for that location, regardless of the other tokens.
+To solve this problem, we have ignored those tokens in our calculations.
+Second run of the Empirical Bayes resulted with an accuracy rate of 0.05.
+When we applied the location whitelist, we have achieved an accuracy of 0.11.
+Which doesn't seem better than making random classifications for 8 locations or picking the location which occurred the most.
+So our experiment with Empirical Bayes classifier failed to produce results better than random, but it helped us understand the data and what kind of filters we need to apply.
 
 \subsection{Scikit Learn - Multinomial Naive Bayes}
-This experiment uses the Multinomial Naive Bayes model to predict classes.
+This experiment uses the Multinomial Naive Bayes(NB) model implemented in Scikit Learn \cite{scikit-learn}(sklearn, v0.17) to perform multi-class predictions.
 This model captures information on documents as an ordered sequence of tokens\cite{mccallum1998comparison}, using a Multinomial Distribution.
-We have used the method implemented in Scikit Learn\cite{scikit-learn}(sklearn, v0.17).
 
@@
 \section{Conclusion and Discussion}
+To improve Empirical Bayes, we have ignored tokens that are not appearing in a location. This was not a valid solution for this problem!
 In this research we have seen that binary classification on tweet locations can get up to 73\% macro precision.

### 2016-03-10 docs/paper.tex
aesiohaesoih

@@
 \begin{abstract}
+
+We extracted textual features that hint to a user's location by comparing different methods.
+Unlike some of the previous studies, we have only used individual tweet texts, geolocation of those tweets and simplified the question to a binary classification problem.
+Our results are showing up to 74\% recall rates.
+
 % Previous research on Twitter user location classification is mostly focusing on multi-class prediction.
@@
 Also the algorithms and the implementations become more complicated.
-Thus, in cases where we just want to know if someone is within a state/city/borough or not, this approach becomes unnecessarily heavy.
+Thus, in cases where we just want to know if someone is within a state/city/borough, this approach becomes unnecessarily heavy.
 In this research, we are simplifying this problem by using binary classification algorithms, which are trying to determine if a tweet sent within the boundaries of a location(i.e.
-Manhattan, NY) or not.
+Manhattan, NY).
 
 Revolving around our hypothesis, the research question we're trying to answer is: "Are there textual features in tweets, that are common for people within the same location?
-If there are, can they help us determine if a tweet is sent within that high-level location, or not?"
+If there are, can they help us determine if a tweet is sent within that high-level location?"
 
@@
 
-% Using text mining methods and location tags in tweets, \cite{cheng2010you} redefined this problem.
-\cite{cheng2010you} used only the text data and introduced a method that identifies the words with strong local geo-scope.
-This study achieved up to 51\% accuracy to locate users within a 100 mile radius.
+Similar to our work, using textual features in tweets and geotags, Cheng et al.approached this question as a regression problem\cite{cheng2010you}.
+They have located users within a 100 mile radius and achieved up to 51\% accuracy.
+To do that, they used only the textual features and introduced a method that identifies these features(i.e.
+unique words) with strong local geo-scope.
 
-% \cite{hecht2011tweets} introduced the $CALGARI$ classifying algorithm specific to this problem, focusing on country and state prediction.
+Hecht et al.
+introduced the $CALGARI$ classification algorithm specific to this problem, focusing on a higher granularity of country and state prediction\cite{hecht2011tweets}.
 They got a 72\% accuracy for classifying 4 countries and 30\% accuracy on classifying 18 states.
+Their method was depending on the location information revealed by users in their tweets, and classifying user's location based on their past tweets.
 
-% \cite{eisenstein2010latent} created a geographic topic model to make use of the textual differences in topics based on regions, they got a median distance error of 494 kms.
+Eisenstein et al.
+created a model using textual features in different topics(e.g.
+Sports, Entertainment)\cite{eisenstein2010latent}.
+Their research got a median distance error of 494 km for individual tweets.
 
-% \cite{wing2011simple} tried to solve this problem using geotagged Wikipedia articles and tweet texts, focusing on predicting the geolocation.
-Their work has obtained a median error of 479 km's for tweets.
+Wing et al.
+created another model by combining geotagged Wikipedia articles and tweet texts\cite{wing2011simple}.
+They have created geodesic grids varying in size, and they have obtained a median error of 479 km for individual tweets.
 
-% \cite{mahmud2012tweet} introduced hierarchical classification methods combined with statistical methods.
-They have achieved 58\%, 66\% and 78\% accuracy on city, state and timezone levels, respectively.
-Also their findings show that users may be able to partially hide their locations, making their tweets untraceable.
-Same researchers revisited the problem in \cite{mahmud2014home}, trying to classify the home location of users, achieving similar results and also introducing movement and location prediction.
+Mahmud et al.
+introduced hierarchical classification methods combined with statistical methods\cite{mahmud2012tweet}.
+They have used tweet texts as well as tweeting behaviour to achieve 58\%, 66\% and 78\% accuracy on city, state and timezone levels, respectively.
+Same researchers revisited the problem in, trying to classify the home location of users, achieving similar results and also introducing movement and location prediction\cite{mahmud2014home}.
 
-% \cite{sadilek2012finding} approached this problem introducing the friend information, constructing a friend location graph.
-Their study was able to achieve 77\% to 84.3\% accuracy, relative to available number of friends.
-
-% \cite{graham2014world} studied the problems with the baselines accepted by recent studies and explained why location and language classification is not an easy problem and how some of the assumptions are incorrect, such as accepting the device location as user's location.
+Also, Graham et al.
+studied the problems with the baselines accepted by recent studies and explained why location and language classification is not an easy problem and how some of the assumptions are incorrect, such as accepting the device location as user's location\cite{graham2014world}.
 
@@
 
-When we applied all these filters, we ended up having a dataset containing 8 locations, each of them having between 986 to 180 tweets, summing up to 3176.
+When we applied all these filters, we ended up having a dataset containing 8 locations, each of them having between 976 to 212 tweets, summing up to 3176.
 
@@
 
-In all our experiments, we have splitted our datasets 50\% by 50\% training and test datasets.
+In all our experiments, we have splitted our datasets 0.5 by 0.5 training and test datasets.
 \subsection{Tools}
@@
 \end{equation*}
-To train this algorithm, we have created a likelihood($p(t | L)$) and an empirical prior.
+To train this algorithm, we created a likelihood($p(t | L)$) and an empirical prior.
 To calculate the likelihood, we have tokenized each tweet using the $twokenize$ module\cite{gimpel2011part}, labelled them with the location and calculated the "probability of a token given location".
@@
 
-To test the assumption we made to enrich our dataset, this experiment was ran with 2 configurations one using past tweets and other using sampled tweets.
-In the first configuration, we labelled each past tweet with the high-level location of the related sample(tweet).
-We have used this configuration to test our assumption of users are always sending tweets within same high-level location, thus we can use their pasts.
+To test our assumption about past tweets, this experiment was ran with 2 configurations one using past tweets and other using sampled tweets.
+In the first configuration, we combined each past tweet to one document and labelled them with the high-level location of the related sample(tweet).
+We have used this configuration to test our assumption of users are always sending tweets within same high-level location.
 In the second configuration, we only used the sample tweets and their high-level locations as labels.
 
-First run of the experiment, without applying filters to the dataset, resulted with 0.02 and 0.04 accuracy rates for the first and second configurations, respectively.
-After this experiment, we have seen that the assumption on the first configuration did not improve our results, so this is not likely to be true.
-The rest of this Empirical Bayes experiment was ran only with the sampled tweets.
+First run of the experiment, without applying filters to the dataset, resulted with 0.02 and 0.04 macro-average precision rates for the first and second configurations, respectively.
+After this experiment, we have seen that the assumption about past tweets did not improve our results.
+The rest of this Empirical Bayes experiment was ran only with the second configuration, sampled tweets.
 
 One problem with this experiment was, if a token($t_x$) didn't appear in the training dataset, we didn't know the likelihood of that token.
-So if tweet contains a token which did not appear on that location in training, that tweet got a probability of 0 for that location, regardless of the other tokens.
+So if there is a token did not appear in the training, the tweets containing that token got a probability of 0 for all locations, regardless of the other tokens.
 To solve this problem, we have ignored those tokens in our calculations.
-Second run of the Empirical Bayes resulted with an accuracy rate of 0.05.
-When we applied the location whitelist, we have achieved an accuracy of 0.11.
+This solution, is not mathematically correct because ignoring a token means setting it's probability to 1.
+Still, replacing those probabilities improved the macro-average precision to 0.05.
+
+When we applied the location whitelist, we have achieved a macro-average precision of 0.11.
 Which doesn't seem better than making random classifications for 8 locations or picking the location which occurred the most.
-So our experiment with Empirical Bayes classifier failed to produce results better than random, but it helped us understand the data and what kind of filters we need to apply.
 
-\subsection{Scikit Learn - Multinomial Naive Bayes}
-This experiment uses the Multinomial Naive Bayes(NB) model implemented in Scikit Learn \cite{scikit-learn}(sklearn, v0.17) to perform multi-class predictions.
-This model captures information on documents as an ordered sequence of tokens\cite{mccallum1998comparison}, using a Multinomial Distribution.
+So our experiment with Empirical Bayes classifier failed to produce results better than any baseline, but it helped us understand the nature of data and what kind of filters we need to apply.
 
-Also, in this experiment, we have redefined the data configurations.
-For the first data configuration, all tweets of a user are tagged with the original tweet's geotag location.
-For the second configuration, we have ignored the user history and only used the geotagged tweets.
+\subsection{Scikit Learn - Experiment Setup}
+After failing to produce results better than making random choices, we decided to use the Scikit Learn \cite{scikit-learn}(sklearn, v0.17) library to actually test our hypothesis using binary classification and compare our results with multi-class classification.
 
-These implementations also had a different structure.
-Instead of token counts used in the first experiment, we have used tf-idf scores.
-Also sparse matrix implementation of Numpy is used to represent those frequencies by default.
-We have stopped using the $twokenize$ module and switched to the internal tokenizer of sklearn.
+In this set of experiments, we have re-define our experiment setting.
+Since we started using a library, we have access to more complicated tools which helps us to define better experiment settings.
+This experiment uses sparse arrays to represent tweets.
+For each tweet, there is a 1 dimensional sparse array with columns representing tokens(in our dataset).
+Combining these, we have created two 2 dimensional sparse arrays, representing our training and test datasets.
+As for the values representing tokens, we have used tf-idf scores.
+
+We chose tf-idf scores because we wanted to reduce the importance of stopwords and frequently used words.
+This experiment learns idf scores from the training dataset, and uses these scores to calculate the tf-idf scores for training and test datasets.
+
+Using tf-idf scores and sparse arrays, we can't capture textual features created by a sequence of words.
+A good example to that would be \textit{The Empire State}.
+\textit{The}, \textit{Empire} and \textit{State} are words that could be used without a spatial context.
+Our sparse array would only contain individual information about the tf-idf scores of these tokens.
+So we are losing the information of using them together, which may be a textual feature, pointing to Manhattan, New York.
+
+To overcome this limitation, we included word ngram tf-idf scores in our sparse arrays.
+Doing so we got information about word sequences, which would possibly solve the problem.
+We have experimented with 2 configurations, first one using only the tokens or word unigrams, second one using  word unigrams with word bigrams.
+
+We also tried to make use of past tweets by labelling them individually with the location of their sample tweet.
+We created 2 configurations for this, one using the sample tweets, other using the sample tweets.
+
+Putting it all together, we had 8 different configurations, combining the word ngrams, past/sample tweets and binary/multiclass classification.
+Again using the 0.5 by 0.5 split for train and test datasets.
 
@@
 
-For this experiment, MultinomialNB(Multinomial Naive Bayes) implementation is selected.
-This implementation has achieved a higher macro accuracy results of 0.19, 0.24 for first and second configurations, respectively.
-But when we investigated the accuracy we have seen that the classifier almost always predicted the location with highest amount of tweets.
+To test our experiment setup, we chose MultinomialNB(Multinomial Naive Bayes) implementation for multi-class classification. MultinomialNB considers the
+
+This implementation has achieved higher macro-average precision results compared to our Empirical Bayes experiment.
+Using unigrams to perform multi-class classification, we had macro-average precisions 0.19, 0.24 using past tweets and sample tweets, respectively.
+But when we investigated the predictions, we have seen that the classifier was almost always predicting the location with highest amount of tweets(Manhattan, NY).
 
 \subsubsection{Normalisation of Documents per Class}
-To prevent the problem in the last experiment, we have normalised the dataset by accepting equal amount of documents per class.
-Upon normalising the number of documents per class, we have achieved accuracy rates of 0.29, 0.42 for first and second data configurations.
-
-\subsubsection{Ngrams}
-To improve the results found in the last experiment, we have tried Ngrams in range (1,2).
-It did not result with an improvement in accuracy.
-The accuracy has decreased by 0.003 for both configurations.
-
-\subsubsection{Binary Classification}
-To be able to answer the question, which tweets are from given a location, we have changed our multi-class classification problem to a binary classification problem.
-Running tests to classify tweets from $Manhattan,\ NY$ by including previous improvements and ngrams in range (1,2) we have achieved accuracy rates of 0.71, 0.62 for first and second data configurations, respectively.
+To prevent the problem we faced in MultinomialNB test, we have normalised the dataset number of documents per class.
+To do so, we normalized the number of documents per class by limiting the \textit{maximum number of documents per class} to the \textit{class with least amount of documents}.
+That reduced the elements in our training dataset to \textit{number of classes}(8) times \textit{number of documents in class with least documents}(e.g.
+\textit{Atlanta, GA} with 122 samples)  for multi-class configuration.
+For binary classification, we have used the class with maximum number of documents(e.g.
+\textit{Manhattan, NY} with 976 samples), and combined it with same amount of random samples for non-class training data.
+Upon normalisation, our multi-class training dataset shrank considerably, but we have achieved macro-average precision rates of 0.29, 0.42 for past tweets and sample tweets, using unigrams.
 
 \subsection{Scikit Learn - Algorithm Comparison}
-This experiment compares the classification methods implemented in Scikit Learn(sklearn)(v0.17) library with different configurations.
-Sklearn implements various classification methods such as, Logistic Regression, Perceptron, Support Vector Classifiers and etc.
-We have compared the sklearn methods under supervised learning\footnote{http://scikit-learn.org/stable/supervised\_learning.html}, applicable to classification and able to work with sparse matrices.
-We have also tried various parameters for those algorithms.
-Resulting set of algorithms and parameters was containing 22 combinations.
+To see which approach is best for our research question and what kind of token based textual features are useful for our task, we compared some classification methods implemented in Scikit Learn\footnote{http://scikit-learn.org/stable/supervised\_learning.html}.
+Scikit Learn implements various classification methods such as, Logistic Regression, Perceptron, Support Vector Classifiers and etc.
+
+Scikit Learn implements different model configurations.
+A good example is, the loss function of SGDClassifier.
+There are 9 different loss functions implemented that we could use with SGDClassifier.
+In our experiment, we tried to capture some of these different parameters, and tried to explain them.
+But in most cases, we didn't try to fine tune the hyper-parameters.
 
@@
 
-\item LogisticRegressionCV: a linear model for classification.
-Uses a logistic function to calculate the class probabilities are of a single trial.
-This version uses cross validation to find optimal values for parameters.
-\item SGDClassifier: Stochastic Gradient Descent learning model supporting multiple loss functions and penalties. 
+\item LogisticRegressionCV: Uses a logistic function that combines the tf-idf scores with weights in a logistic function. This model is useful if our tf-idf scores have exponential effects.
+\item SGDClassifier: Stochastic Gradient Descent creates a linear function and gives initial weights to each token for each class.
+Based on the loss functions defined below, it tries to optimize these weights.
 \begin{enumerate}
-\item SGDClassifier(loss="hinge"): Hinge is a commonly used convex loss function for classification.
+\item SGDClassifier(loss="hinge"): Hinge is a commonly used linear loss function for classification.
 \item SGDClassifier(loss="log"): Converts SGD to a probabilistic logistic regression classifier.
@@
 \end{enumerate}
-\item Perceptron: Same as SGDClassifier(loss="perceptron") with a constant learning rate and different default parameters.
-\item PassiveAggressiveClassifier: Similar to Perceptron. Instead of using a learning rate, uses a regularisation term.
+\item Perceptron: Same as SGDClassifier(loss="perceptron"), updates the tf-idf weights with a constant learning rate and has different default parameters.
+\item PassiveAggressiveClassifier: Similar to Perceptron. Instead of using a learning rate, uses a regularisation term that makes sure that tf-idf weights don't get too big and prevents overfitting.
 \begin{enumerate}
@@
 \end{enumerate}
-\item SVC: Classifier model using Support Vector Machines. Creates a high or infinite dimensional one or many hyperplanes and clusters classes on that space.
+\item SVC: Classifier model using Support Vector Machines. Converts tf-idf scores based on the kernel function to create a high or infinite dimensional hyperplanes by clustering classes on that space.
 \begin{enumerate}
@@
 \end{enumerate}
-\item LinearSVC: SVM with linear kernel.
-\item KNeighborsClassifier: K-Nearest Neighbours classifier.
+\item LinearSVC: SVM with a linear kernel.
+\item KNeighborsClassifier: K-Nearest Neighbours classifier, uses weights function to cluster and classify tf-idf scores using the function given in weights.
+Finds the $n_neighbours$ number of tweets with most similar tokens from training dataset, casts a vote among them make predictions.
 \begin{enumerate}
@@
 \end{enumerate}
-\item MultinomialNB: Multinomial Naive Bayes, assumes a Multinomial Distribution of features.
-\item BernoulliNB: Bernoulli Naive Bayes, assumes a Bernoulli Distribution of features.
+\item MultinomialNB: Gives probabilities for each token and class, combines them to find the most likely class.
+\item BernoulliNB: Similar to Multinomial, but instead of using tf-idf scores, considers if a token occurs in a tweet or not.
 \item DecisionTreeClassifier: Creates a rule based decision tree inferred from data for predict.
@@
 \normalsize
-We have tried those 22 combination of algorithms and parameters, with 3 different data configuration parameters; 
-\footnotesize
-\begin{enumerate}
-\item Binary Classification
-\item Include user history
-\item Ngram
-\end{enumerate}
-\normalsize
+We have tried those 22 models, with 8 configurations to create 176 different combinations.
 
-Resulting with 8 different data configurations and 176 different combinations.
+\subsubsection{Execution}
 
-\subsubsection{Precision, Recall, Fscore}
-To represent the results of those 176 combination, precision, recall and fscore are used.
-\subsubsection{Execution}
-To execute those tasks, we have decided to use Google Cloud instances.
+To execute those tasks, we have used Google Cloud instances.
 Google Cloud offers 300\$ trial usage for users who want to try out their services and it allows up to 32 cores in this trial period.
@@
 Created a template operating system including an executable version of our implementation.
-Created 15 two core execution instances from this template, 1 MongoDB instance to serve data, store results and progress.
-It took 35 mins to finish the execution of those 176 tasks.
+Using 15 two core execution instances from the execution template, 1 MongoDB instance, it took 35 mins to finish the execution of those 176 tasks.
 
 \section{Results}
-Using Scikit-learn\cite{scikit-learn} we tried location classification using 22 models on 8 different settings.
-Those results have been shared in Figure 1 and 2.
-Figures contain 12 subfigures, showing precision, recall and f1scores for different combinations of ngram(1,2) and include user history(0,1) parameters.
-Each figure contains the relative results for 22 different models using the Box plots\cite{mcgill1978variations}.
-Each box plot shows outliers with plusses(+), max and min value as dashes, a bounding box of upper and lower quartiles, a red dash showing the mean(instead of median).
-Because each class contains equal amount of data, mean of precision, recall and f1score can be interpreted as the macro precision, recall and f1score.
-Each subfigure contains a green line indicating the baseline macro precision, recall or f1score.
-In subfigures, models have been labelled with numbers ranging between 0 and 21.
-Those labels are given in Table 1.
 
-Tall boxes in the figures represent unstable results, mostly caused by models predicting one or more classes better than others or failing to classify one or more classes not as good as others.
+\subsection{Binary Classification Baselines}
+We have considered 2 baselines to compare our results for predicting \textit{Manhattan, NY}. First one is making random choices with a baseline macro-average precision/recall and f1-score of 0.5.
 
-\begin{table}
-\scriptsize
-    \begin{tabular}{|c|l||c|l|}
-	\hline 
-		0 & LogisticRegressionCV & 1 & SGDClassifier(loss="hinge") \\ \hline
-		2 & SGDClassifier(loss="log")&  3 & SGDClassifier(loss="modified\_huber") \\ \hline
-		4 & SGDClassifier(loss="squared\_hinge") & 5 & SGDClassifier(loss="perceptron") \\ \hline
-		6 & SGDClassifier(loss="squared\_loss") & 7 & SGDClassifier(loss="huber")\\ \hline
-		8 &SGDClassifier(loss="epsilon\_insensitive") & 9 & SGDClassifier(loss="squared\_epsilon\_insensitive") \\ \hline
-		10 & Perceptron & 11 & PassiveAggressiveClassifier(loss="hinge")\\ \hline
-		12 & PassiveAggressiveClassifier(loss="squared\_hinge") & 13 & SVC(kernel="poly") \\ \hline
-		14 & SVC(kernel="sigmoid") & 15 & LinearSVC\\ \hline
-		16 & KNeighborsClassifier(weights="uniform") & 17 & KNeighborsClassifier(weights="distance") \\ \hline
-		18 & MultinomialNB & 19 & BernoulliNB\\ \hline
-		20 & DecisionTreeClassifier & 21 & AdaBoostClassifier\\ \hline
-	\end{tabular}
-	\caption{Classifier Model Labels}
-\end{table}
-\normalsize
-\subsection{Parameters}
+The second baseline is through choosing tweets containing important keywords.
+To do so, we have created a regular expression and ran it through out dataset.
+This regular expression created a baseline macro-average precision of 0.8.
+Compared to the high macro-average precision, it had a very low recall 0.37 for predicting our location, \textit{Manhattan, NY}.
+Since we are interested in being able to say if a tweet is sent within a location, we're not going to use this baseline for comparison.
 
-\subsubsection{Ngram}
-Effects of including token bigrams with unigrams did not have major implications in the results. This parameter has changed the average f1scores of models by +0.04 to -0.05.
+\begin{verbatim}
+.*(([Mm]anhattan)|([Nn]ew[ ]?[Yy]ork)|(NY)).*
+\end{verbatim}
 
-\subsubsection{Including User History}
-Including history in the training and testing phases reduced the classifier performances in almost all cases. Overall average decrease in f1scores was 0.076 with values 
-ranging from 0.21 to -0.09.
+Combining the random baseline and regular expression, we have created a new baseline.
+In this baseline, if the regular expression matches we classify this data as \textit{Manhattan, NY}, otherwise we make random choices.
+This combined baseline gives us a 0.68 recall, 0.57 precision and 0.62 f1-score for \textit{Manhattan, NY} with 0.59 macro-averaged recall, 0.59 macro-averaged precision and 0.59 macro-averaged f1-score.
+
+\subsection{Binary Classification}
+
+Including bigrams, BernoulliNB, SGD with modified huber loss function and SGD with hinge loss function have achieved the top 3 macro-averaged f1scores of 0.734, 0.726, 0.72, respectively.
+
+Only with unigrams BernoulliNB, MultinomialNB and PassiveAgressiveClassifier with hinge loss function achieved the top 3 macro-averaged f1scores of 0.726, 0.719 and 0.717, respectively.
 
 \subsection{Multi-Class Classification}
-Baseline for Multi-Class classification is 0.125.
-Since we have 8 classes in total for this task, if a model has predicted only one class, that baseline value would be the macro precision, recall and f1score.
-For this task, top result was achieved by LogisticRegressionCV with an fscore of 0.443 and a recall of 0.50.
+Random baseline compared with location names(as in the for 8 locations and
 
-\subsection{Binary Classification}
-Baseline for this task is 0.5. With bigrams, BernoulliNB, SGD with modified huber loss function and SGD with hinge loss function have achieved the top 3 f1scores of 0.734, 0.726, 0.72, respectively. 
-Only with unigrams BernoulliNB, MultinomialNB and PassiveAgressiveClassifier with hinge loss function achieved the top 3 f1scores of 0.726, 0.719 and 0.717, respectively.
+\subsection{Assumption of Past Tweets}
+Using past tweets as our dataset reduced the classifier performance of almost all configurations.
+Overall average decrease in f1scores was 0.076 with values ranging from 0.21 to -0.09.
+Our assumption was wrong.
 
-\section{Conclusion and Discussion}
-To improve Empirical Bayes, we have ignored tokens that are not appearing in a location. This was not a valid solution for this problem!
-In this research we have seen that binary classification on tweet locations can get up to 73\% macro precision.
-Compared to previous studies dealing with this problem in a multi-class perspective, if the task is to predict if a tweet is belonging to one particular location, this looks like a promising result.
-But the fact of all our data belonging to geotagged tweets may compromising the validity of these results.
+\subsection{Textual Features}
 
-Refining the training dataset with less application generated content and more data would yield with more authentic research result.
-\noindent\begin{sidewaysfigure}
-    \centering
-    \includegraphics[width=\paperwidth]{figures/binary.eps}
-    \caption{Binary classification results}
-\end{sidewaysfigure}
-\noindent\begin{sidewaysfigure}
-    \centering
-    \includegraphics[width=\paperwidth]{figures/multi_class}
-    \caption{Multi-Class classification results}
-\end{sidewaysfigure}
-\newpage
+When we investigated why BernoulliNB is achieving the highest performance, we have seen that in most of the cases(around 90\% of the correct predictions), there was a building or place name included in the tokens(e.g.
+\textit{Central Park}, \textit{Empire State}).
+In the rest of the cases(around 10\%), there were no obvious textual features.
+In those cases we assumed that there was a unique token that only appeared in tweets labelled as \textit{Manhattan, NY}.
+BernoulliNB is the simplest of all, it only considers if a token appears in a location or not.
 
+\section{Conclusion}
+
+In our research question, we asked if there are any textual features that are shared by the people who are within a high-level location.
+In our experiments, we couldn't find any specific linguistic or textual features in English that hints to the geolocation(i.e.
+\textit{Manhattan, NY}) of a tweet, except the location names.
+
+Using the location names included in tweets, were able to improve the combined baseline(macro-averaged f1score) for binary classification around 0.16.
+
+\section{Discussion}
+
+The fact of all our data was geotagged may be adding a bias to our dataset and compromising the validity of our results.
+It may be possible for geotagged tweets to include more location names.
+Refining the training dataset with more user generated content(i.e.
+removing Foursquare or Yelp from source whitelist) and collecting more data would yield more authentic results and more textual features.
+
+We have seen that BernoulliNB had one of the top results in binary classification.
+This hints to having tf-idf scores may not be a good idea, because this method ignores these scores and uses binary values.
+Instead of having tf-idf scores, having binary values in the sparse array and trying different configurations on this dataset might yield to a better improvement on the baseline.
+But as we have concluded, we couldn't see any unique words that identify the high-level location of user.
+
+To improve Empirical Bayes, we have ignored tokens that are not appearing in a location.
+This solution was wrong because it sets the likelihood to 1 when it can't find a token on a location.
+A solution would be setting the likelihood as if that token appeared only once.
 \bibliographystyle{alpha}

### 2016-03-10 docs/paper.tex
for review

@@
 \subsection{Multi-Class Classification}
-Random baseline compared with location names(as in the for 8 locations and
+Random baseline combined with obvious location names, for 8 locations, gives us a macro-averaged f1-score of  0.17.
+In our experiments with multi-class classification, we were able to improve this score to 150\% using SGDClassifier with different loss functions.
 

### 2016-03-10 docs/paper.tex
abstract revisited

@@
 
-We extracted textual features that hint to a user's location by comparing different methods.
-Unlike some of the previous studies, we have only used individual tweet texts, geolocation of those tweets and simplified the question to a binary classification problem.
-Our results are showing up to 74\% recall rates.
-
-% Previous research on Twitter user location classification is mostly focusing on multi-class prediction.
-Approaching at the same problem from another perspective, in some cases, it may be enough to answer if someone belongs to a location or not.
-In this perspective, we have compared some models for predicting tweet locations using Binary and Multi-Class Classification.
-We have seen that if the problem at hand is reducible to Binary Classification, it is possible to make much better predictions.
+We extracted textual features from tweets which hint to the location it was sent from.
+Unlike some of the previous studies, we have only used individual tweet texts and geolocation of those tweets.
+We have also simplified the question to a binary classification problem.
+Our results are showing up to 74\% recall rates in classifying if a tweet is sent from Manhattan, NY.
 
@@
 Thus, in cases where we just want to know if someone is within a state/city/borough, this approach becomes unnecessarily heavy.
-In this research, we are simplifying this problem by using binary classification algorithms, which are trying to determine if a tweet sent within the boundaries of a location(i.e.
+In this research, we are simplifying this problem by using binary classification algorithms, which are trying to determine if a tweet is sent within the boundaries of a location(i.e.
 Manhattan, NY).

### 2016-03-10 docs/paper.tex
i i did intro

@@
 
-Twitter is an online platform that lets users to share posts with their followers, limited with at most 140 characters, called as tweets.
-Tweets can be almost anything that we share on internet; a personal message stating our views, a link to an article, a picture and etc..
+Twitter is an online platform that lets users share posts with their followers, limited to at most 140 characters, called tweets.
+Tweets can be almost anything that we share on the internet, for example: a personal message stating our views, a link to an article or a picture.
 There are no boundaries except the character limit.
-In 2009, Twitter introduced an option to include geographic location(geolocation) information on tweets\footnote{\url{https://blog.twitter.com/2009/location-location-location}}.
-Since then, a lot of twitter users have been sharing their geolocation with their tweets(or geotagging their tweets).
+In 2009, Twitter introduced an option to include geographic location (geolocation) information with tweets\footnote{\url{https://blog.twitter.com/2009/location-location-location}}.
+Since then, a lot of twitter users have been sharing their geolocation with their tweets (or geotagging their tweets).
 Depending on the context of the tweet, having the geolocation may be very valuable.
 For example a tweet about a Pizza franchise or a political campaign, if geotagged, may point to an improvement with exact location or contribute to the statistics of a specific area.
-Unfortunately, geolocation of a tweet is not shared by default or in other words, most of the tweets are not geotagged, unless explicitly specified.
+Unfortunately, geolocation of a tweet is not shared by default.
+In other words, most of the tweets are not geotagged, unless explicitly specified.
 Inferring the geolocation of a tweet is what this paper is about.
 
-To be able to infer this information, we can try to use linguistic habits shared by the people who are within the same location.
+To be able to infer this information, we can try to use linguistic habits shared by the people who are in the same location.
 As humans, our spatial cognition deals with updating and managing the knowledge about our environment.
-Spatial cognition changes when we move between environments, but as we stay within the boundaries of a high level environment(i.e.
+Spatial cognition changes when we move between environments, but as we stay within the boundaries of a high-level environment(i.e.
 state, city, borough), there may be some high-level constants that doesn't change.
@@
 
-Revolving around our hypothesis, the research question we're trying to answer is: "Are there textual features in tweets, that are common for people within the same location?
-If there are, can they help us determine if a tweet is sent within that high-level location?"
+Revolving around our hypothesis, the research question we're trying to answer is: "Are there textual features in tweets, that are common for people in the same location?
+And if there are, can they help us determine if a tweet is sent within that high-level location?"
 

### 2016-03-13 baseline.py
check baseline condition

@@ -1,0 +1,40 @@
+import re
+
+from data.Data import Data
+
+p = re.compile('.*(([Mm]anhattan)|([Nn]ew[ ]?[Yy]ork)|(NYC)|((NY))).*')
+
+d = Data(training_factor=0, include_user_history=False)
+docs = d.get_training_data()
+docs = d.get_test_data()
+matchCount = 0
+count = 0
+nyc = 0
+nyc_corr = 0
+nyc_incorr = 0
+not_nyc = 0
+not_nyc_corr = 0
+not_nyc_incorr = 0
+for doc in docs:
+    m = p.match(doc["text"])
+    match = m is not None
+    is_nyc = doc["place"]["full_name"] == "Manhattan, NY"
+
+    nyc += is_nyc
+    nyc_corr += is_nyc and match
+    nyc_incorr += is_nyc and not match
+    not_nyc += not is_nyc
+    not_nyc_corr += not is_nyc and not match
+    not_nyc_incorr += not is_nyc and match
+
+print nyc
+print nyc_corr
+print nyc_incorr
+
+print not_nyc
+print not_nyc_corr
+print not_nyc_incorr
+
+
+print "micro-average precision: %.2f" % ((nyc_corr + not_nyc_corr) / (nyc + not_nyc))
+print "micro-average recall: %.2f" % ((nyc_corr + not_nyc_corr) / (nyc + not_nyc))
